---
title: "simulation-plots"
author: "Leonardo Feitosa"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
library(tidyverse)
library(here)
library(patchwork)
library(gt)
library(paletteer)

# file path
basedir <- "G:/Meu Drive/PhD Project - Fisheries bycatch/Bycatch project/Chapter 1/analyses/"
outdir <- file.path(basedir, "model_outs") # calls present data from raster files
```

```{r, include = FALSE}
# Results from the parameter per parameter simulations
#output_price_ranges <- read_csv(file.path(outdir, "output_price_ranges.csv"))

output_growth_ranges <- read_csv(file.path(outdir, "output_r_ranges.csv"))

output_q_ranges <- read_csv(file.path(outdir, "output_q_ranges.csv"))

#output_full <- read_csv(file.path(outdir, "output_full.csv"))
```

```{r}
# Updated dataset to be used in the analyses
output_test <- read_csv(file.path(outdir, "output_ranges_test.csv"))  

output_test_updated <- output_test %>% 
  pivot_wider(names_from = "variables",
              values_from = "values") %>% 
  mutate(b_values_s = N_s / k_s,
         b_values_w = N_w / k_w) %>% 
  pivot_longer(cols = e:N_w,
               names_to = "variables",
               values_to = "values") %>% 
  pivot_longer(cols = starts_with("b_values"),
               names_to = "b_stocks",
               values_to = "b_v_k") %>% 
  mutate(vuln_ratio = (q_s/r_s) / (q_w/r_w))
```

```{r, echo = FALSE}
head(output_test_updated, n = 20) %>% 
  gt() %>% 
  tab_header(title = "Glimpse of the first 20 rows of the dataset") %>% 
 cols_align(align = "center")
```


# Results from the parameter per parameter simulation



```{r, include = FALSE}
# output_price_ranges %>%
#   pivot_wider(names_from = "stock_prices",
#               values_from = "prices") %>% 
#   filter(variables %in% c("N_w", "N_s")) %>% 
#   ggplot() +
#   geom_raster(aes(x = p_w, y = p_s, fill = values)) +
#   facet_wrap(~ variables) +
#   scale_fill_gradientn(name = "Weak stock size", 
#                        colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   scale_x_continuous(breaks = seq(0, 10, 1)) +
#   scale_y_continuous(breaks = seq(0, 10, 1)) +
#   labs(x = "Weak stock price range",
#        y = "Strong stock price range",
#        title = "Simulation of price ranges on variable size") +
#   theme_bw() 
```

```{r, include = FALSE}
# output_price_ranges %>%
#   pivot_wider(names_from = "stock_prices",
#               values_from = "prices") %>% 
#   filter(variables %in% c("N_w", "N_s")) %>% 
#   ggplot() +
#   geom_raster(aes(x = p_w, y = p_s, fill = values)) +
#   facet_wrap(~ variables) +
#   scale_fill_gradientn(name = "Weak stock size", 
#                        colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   scale_x_continuous(breaks = seq(0, 10, 1)) +
#   scale_y_continuous(breaks = seq(0, 10, 1)) +
#   labs(x = "Weak stock price range",
#        y = "Strong stock price range",
#        title = "Simulation of price ranges on variable size") +
#   theme_bw() 
```




```{r, include = FALSE}
# output_price_ranges %>%
#   pivot_wider(names_from = "stock_prices",
#               values_from = "prices") %>% 
#   ggplot() +
#   geom_raster(aes(x = p_w, y = p_s, fill = values)) +
#   facet_wrap(~ variables) +
#   scale_fill_gradientn(name = "Weak stock size", 
#                        colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   scale_x_continuous(breaks = seq(0, 10, 1)) +
#   scale_y_continuous(breaks = seq(0, 10, 1)) +
#   labs(x = "Weak stock price range",
#        y = "Strong stock price range",
#        title = "Simulation of price ranges on variable size") +
#   theme_bw() +
#   theme(panel.spacing = unit(4, "mm"))
```



```{r, include = FALSE}
# output_q_ranges %>%   
#   pivot_wider(names_from = "stock_q",
#               values_from = "q") %>%  
#   ggplot() +
#   geom_raster(aes(x = q_w, y = q_s, fill = values)) +
#   facet_wrap(~ variables,
#             scales = "free_y") +
#   scale_fill_gradientn(name = "stock size", colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   facet_wrap(~ variables,
#              scales = "free_y") +
#   labs(x = "Weak stock q ranges",
#        y = "Strong stock q ranges",
#        title = "Simulation of catchability ranges on stock size") +
#   theme_bw() 
```



```{r, include = FALSE}
# output_full %>% 
#   filter(variables %in% c("N_w", "N_s")) %>% 
#   pivot_longer(cols = starts_with("values_"),
#                names_to = "parameter",
#                values_to = "values") %>%  
#   filter(parameter == "values_price") %>% 
#   ggplot() +
#   geom_point(aes(x = price_ratio, y = log(prod_ratio + 1), color = values),
#              alpha = 0.6) +
#   scale_color_gradientn(name = "stock size", colors = RColorBrewer::brewer.pal(5, "YlOrRd")) +
#   labs(x = "Price ratio (p_s/p_w)",
#        y = "Vulnerability ratio (q_s/r_s)/(q_w/r_w)",
#        title = "Simulation of the distribution of productivity and price ratios") +
#   theme_bw()
```

## Model equations:

- Strong stock size ($N_s$)

$$
N_s = r_s (1 - \frac{N_s}{K_s}) - q_s E
$$

- Weak stock size ($N_w$):

$$
N_w = r_w (1 - \frac{N_w}{K_w}) - q_w E
$$

- Effort ($E$):

$$
E = (p_s q_s N_s + p_w q_w N_w) - C
$$

## Equilibrium points for the three variables:

- Strong stock ($N_s$):

$$
N_s = \frac{K_s * (c * q_s * r_w + K_w * p_w * q_w * (q_w * r_s - q_s * r_w))} {(K_w * p_w * q_w^2 * r_s + K_s * p_s * q_s^2 * r_w)}
$$

- Weak stock ($N_w$):

$$
N_w = \frac{K_w * (c * q_w * r_s + K_s * p_s * q_s * (- q_w * r_s + q_s * r_w))} {(K_w * p_w * q_w^2 * r_s + K_s * p_s * q_s^2 * r_w)}
$$

- Effort ($E$):

$$
E = \frac{(-c + K_s * p_s * q_s + K_w * p_w * q_w) * r_s * r_w} {K_w * p_w * q_w^2 r_s + K_s * p_s * q_s^2 * r_w}
$$

### List of parameters:
- K = carrying capacity
- r = per capita growth rate
- q = catchability of stocks
- c = cost of fishing
- p = price

### Parameter space for both species:

- Catchability (q) varies from 0.1 to 0.5 at intervals of 0.2 for both species.
- Growth rate (r) varies from 0.35 to 1.05 at intervals of 0.35 for the strong stock and from 0.1 to 0.3 at intervals of 0.1 for the weak stock.
- Carrying capacity (k) varies from 3 to 5 at intervals of 1 for the strong stock and from 1 to 3 at intervals of 1 for the weak stock.
- Price ranges (p) from 0.1 to 10 at intervals of 0.5 for both species.


### Distribution of variable values

```{r, echo = FALSE, message = FALSE}
out_full <- 
  output_test_updated %>% 
  # pivot_longer(cols = p_s:k_w,
  #              names_to = "param",
  #              values_to = "param_val") %>% 
  ggplot() +
  geom_histogram(aes(x = values, fill = variables),
                 show.legend = F) +
  facet_wrap(~ variables,
             scales = "free") +
  labs(title = "Full dataset") +
  theme_bw()
```

```{r, echo = FALSE}
out_transf <- 
  output_test_updated %>%
  filter(variables %in% c("N_w", "N_s")) %>% 
  mutate(values = case_when(
    values < 0 ~ 0,
    TRUE ~ values
  )) %>% 
  # pivot_longer(cols = p_s:k_w,
  #              names_to = "param",
  #              values_to = "param_val") %>% 
  ggplot() +
  geom_histogram(aes(x = values, fill = variables),
                 show.legend = F) +
  facet_wrap(~ variables,
             scales = "free") +
  labs(title = "Negative values transformed to zero") +
  theme_bw()
```

```{r, echo = FALSE}
out_pos <- 
  output_test_updated %>%
  filter(values >= 0) %>% 
  # pivot_longer(cols = p_s:k_w,
  #              names_to = "param",
  #              values_to = "param_val") %>% 
  ggplot() +
  geom_histogram(aes(x = values, fill = variables),
                 show.legend = F) +
  facet_wrap(~ variables,
             scales = "free") +
  labs(title = "Negative values filtered out") +
  theme_bw()
```


```{r, fig.height=9, fig.width=9, echo = FALSE}
out_full / 
  (out_transf + out_pos) +
  plot_annotation(title = "Distribution of Equilibria")
```

```{r, echo = FALSE}
out_full_bvk <- 
  output_test_updated %>% 
  # pivot_longer(cols = p_s:k_w,
  #              names_to = "param",
  #              values_to = "param_val") %>% 
  ggplot() +
  geom_histogram(aes(x = b_v_k, fill = b_stocks),
                 show.legend = F) +
  facet_wrap(~ b_stocks,
             scales = "free") +
  labs(title = "Full dataset") +
  theme_bw()
```

```{r, echo = FALSE}
out_transf_bvk <- 
  output_test_updated %>%
  filter(variables %in% c("N_w", "N_s")) %>% 
  mutate(b_v_k = case_when(
    b_v_k < 0 ~ 0,
    TRUE ~ b_v_k
  )) %>% 
  # pivot_longer(cols = p_s:k_w,
  #              names_to = "param",
  #              values_to = "param_val") %>% 
  ggplot() +
  geom_histogram(aes(x = b_v_k, fill = b_stocks),
                 show.legend = F) +
  facet_wrap(~ b_stocks,
             scales = "free") +
  labs(title = "Negative values transformed to zero") +
  theme_bw()
```

```{r, echo = FALSE}
out_pos_bvk <- 
  output_test_updated %>%
  filter(b_v_k >= 0) %>% 
  # pivot_longer(cols = p_s:k_w,
  #              names_to = "param",
  #              values_to = "param_val") %>% 
  ggplot() +
  geom_histogram(aes(x = b_v_k, fill = b_stocks),
                 show.legend = F) +
  facet_wrap(~ b_stocks,
             scales = "free") +
  labs(title = "Negative values filtered out") +
  theme_bw()
```


```{r, fig.height=9, fig.width=9, echo = FALSE}
out_full_bvk / 
  (out_transf_bvk + out_pos_bvk) +
  plot_annotation(title = "Distribution of Equilibria for B/K ratios")
```



### Catchability range simulation


```{r distribution of negative values for Ns and Nw for the range of qs, echo = FALSE}
# New tests with the other parameters also being varied

output_q_ranges %>% 
  pivot_wider(names_from = "stock_q",
              values_from = "q") %>% 
  filter(variables %in% c("N_w", "N_s") & values < 0) %>% 
  ggplot() +
  geom_raster(aes(x = q_w, y = q_s, fill = values)) +
  scale_x_continuous(breaks = seq(0.1, 1, 0.2)) +
  scale_y_continuous(breaks = seq(0.1, 1, 0.2)) +
  facet_wrap(~ variables) +
  scale_fill_gradientn(name = "stock size", colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
  facet_wrap(~ variables,
             scales = "free_y") +
  labs(x = "Weak stock q ranges",
       y = "Strong stock q ranges",
       title = "Simulation of catchability ranges on stock size") +
  theme_bw() 
```


```{r, echo = FALSE}
# output_test_updated %>% 
#   filter(variables %in% c("N_w", "N_s")) %>% 
#   mutate(values = case_when(
#     values < 0 ~ 0,
#     TRUE ~ values
#   )) %>% 
#   ggplot() +
#   geom_raster(aes(x = q_w, y = q_s, fill = values)) +
#   facet_wrap(~ variables,
#             scales = "free_y") +
#   scale_fill_gradientn(name = "Stock size", colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   facet_wrap(~ variables,
#              scales = "free_y") +
#   labs(x = "Weak stock q ranges",
#        y = "Strong stock q ranges",
#        title = "Simulation of catchability ranges on stock size") +
#   theme_bw()
```

```{r, echo = FALSE}
w_s_q <- output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w") %>% 
  ggplot() +
  geom_raster(aes(x = q_w, y = q_s, fill = b_v_k)) +
  #facet_grid(b_stocks ~ variables) + 
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Weak stock q ranges",
       y = "Strong stock q ranges",
       title = "Weak stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
s_s_q <- output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s") %>% 
  ggplot() +
  geom_raster(aes(x = q_w, y = q_s, fill = b_v_k)) +
  #facet_grid(b_stocks ~ variables) + 
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Weak stock q ranges",
       y = "Strong stock q ranges",
       title = "Strong stock",
       fill = "B/K") +
  theme_bw()
```

```{r, fig.width=8, echo = FALSE}
s_s_q + w_s_q +
  plot_annotation(title = "Simulation of catchability ranges on strong and weak stock's B/K ratio - All values")
```


```{r, echo = FALSE}
s_s_q_pos <- output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s" & b_v_k >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = q_w, y = q_s, fill = b_v_k)) +
#  facet_wrap(~ variables) + 
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock q ranges",
       y = "Strong stock q ranges",
       title = "Strong stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
w_s_q_pos <- output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w" & b_v_k >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = q_w, y = q_s, fill = b_v_k)) +
#  facet_wrap(~ variables) + 
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock q ranges",
       y = "Strong stock q ranges",
       title = "Weak stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
s_s_q_pos + w_s_q_pos +
  plot_annotation(title = "Simulation of catchability ranges on B/K ratio - Negative values filtered out")
```


### Price range simulation

```{r, echo = FALSE}
# output_test %>% 
#   filter(values >= 0) %>% 
#   ggplot() +
#   geom_raster(aes(x = p_w, y = p_s, fill = values)) +
#   facet_wrap(~ variables,
#             scales = "free_y") +
#   scale_fill_gradientn(name = "Variable size", colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   facet_wrap(~ variables,
#              scales = "free_y") +
#   labs(x = "Weak stock price ranges",
#        y = "Strong stock price ranges",
#        title = "Simulation of price ranges on variable size") +
#   theme_bw()
```


```{r, echo = FALSE}
ss_p <- output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s") %>% 
  ggplot() +
  geom_raster(aes(x = p_w, y = p_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Weak stock price ranges",
       y = "Strong stock price ranges",
       title = "Strong stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ws_p <- output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w") %>% 
  ggplot() +
  geom_raster(aes(x = p_w, y = p_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Weak stock price ranges",
       y = "Strong stock price ranges",
       title = "Weak stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ss_p + ws_p +
  plot_annotation(title = "Simulation of price ranges on strong and weak stock's B/K ratio - All values")
```


```{r, echo = FALSE}
ss_p_pos <- output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s" & b_v_k >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = p_w, y = p_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock price ranges",
       y = "Strong stock price ranges",
       title = "Strong stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ws_p_pos <- output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w" & b_v_k >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = p_w, y = p_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock price ranges",
       y = "Strong stock price ranges",
       title = "Weak stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ss_p_pos + ws_p_pos +
  plot_annotation(title = "Simulation of price ranges on strong and weak stock's B/K ratio - Positive values")
```

### Growth range simulation

```{r distribution of negative values for Ns and Nw for the range of rs, echo = FALSE}
output_growth_ranges %>% 
  pivot_wider(names_from = "stock_growth_r",
              values_from = "r") %>% 
  filter(variables %in% c("N_w", "N_s") & values < 0) %>% 
  ggplot() +  
  geom_raster(aes(x = r_w, y = r_s, fill = values)) +
  scale_x_continuous(breaks = seq(0, 1.5, 0.2)) +
  scale_y_continuous(breaks = seq(0, 1.6, 0.2)) +
  facet_wrap(~ variables,
            scales = "free_y") +
  scale_fill_gradientn(name = "Stock size", colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
  labs(x = "Weak stock r ranges",
       y = "Strong stock r ranges",
       title = "Simulation of r ranges on variable size") +
  theme_bw() 
```


```{r, echo = FALSE}
# output_test %>% 
#   filter(values >= 0 & variables %in% c("N_w", "N_s")) %>% 
#   ggplot() +
#   geom_raster(aes(x = r_w, y = r_s, fill = values)) +
#   facet_wrap(~ variables,
#             scales = "free_y") +
#   scale_fill_gradientn(name = "Stock size", colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   facet_wrap(~ variables,
#              scales = "free_y") +
#   labs(x = "Weak stock growth ranges",
#        y = "Strong stock growth ranges",
#        title = "Simulation of growth ranges on stock size") +
#   theme_bw()
```

```{r, echo = FALSE}
ss_p <- output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s") %>% 
  ggplot() +
  geom_raster(aes(x = r_w, y = r_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Weak stock growth ranges",
       y = "Strong stock growth ranges",
       title = "Strong stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ws_p <- output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w") %>% 
  ggplot() +
  geom_raster(aes(x = r_w, y = r_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Weak stock growth ranges",
       y = "Strong stock growth ranges",
       title = "Weak stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ss_p + ws_p +
  plot_annotation(title = "Simulation of growth ranges on strong and weak stock's B/K ratio - All values")
```


```{r, echo = FALSE}
ss_r_pos <- output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s" & b_v_k >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = r_w, y = r_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock growth ranges",
       y = "Strong stock growth ranges",
       title = "Strong stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ws_r_pos <- output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w" & b_v_k >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = r_w, y = r_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock growth ranges",
       y = "Strong stock growth ranges",
       title = "Weak stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ss_r_pos + ws_r_pos +
  plot_annotation(title = "Simulation of growth ranges on strong and weak stock's B/K ratio - Positive values")
```

### Carrying capacity range simulation

```{r, echo = FALSE}
# output_test %>% 
#   filter(values >= 0) %>% 
#   ggplot() +
#   geom_raster(aes(x = k_w, y = k_s, fill = values)) +
#   facet_wrap(~ variables,
#             scales = "free_y") +
#   scale_fill_gradientn(name = "Variable size", colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   facet_wrap(~ variables,
#              scales = "free_y") +
#   labs(x = "Weak stock K ranges",
#        y = "Strong stock K ranges",
#        title = "Simulation of K ranges on variable size") +
#   theme_bw()
```


```{r, echo = FALSE}
# output_test %>% 
#   filter(values >= 0 & variables %in% c("N_w", "N_s")) %>% 
#   ggplot() +
#   geom_raster(aes(x = k_w, y = k_s, fill = values)) +
#   facet_wrap(~ variables,
#             scales = "free_y") +
#   scale_fill_gradientn(name = "Stock size", colors = RColorBrewer::brewer.pal(9, "YlOrRd")) +
#   labs(x = "Weak stock K ranges",
#        y = "Strong stock K ranges",
#        title = "Simulation of K ranges on stock size") +
#   theme_bw()
```

```{r, echo = FALSE}
ss_k <- 
  output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s") %>% 
  ggplot() +
  geom_raster(aes(x = k_w, y = k_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock K ranges",
       y = "Strong stock K ranges",
       title = "Strong stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ws_k <- output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w") %>% 
  ggplot() +
  geom_raster(aes(x = k_w, y = k_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Weak stock K ranges",
       y = "Strong stock K ranges",
       title = "Weak stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ss_k + ws_k +
  plot_annotation(title = "Simulation of K ranges on strong and weak stock's B/K ratio - All values")
```



```{r, echo = FALSE}
ss_k_pos <- output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s" & b_v_k >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = k_w, y = k_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock K ranges",
       y = "Strong stock K ranges",
       title = "Strong stock",
       fill = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
ws_k_pos <- output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w" & b_v_k >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = k_w, y = k_s, fill = b_v_k)) +
  scale_fill_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Weak stock K ranges",
       y = "Strong stock K ranges",
       title = "Weak stock",
       fill = "B/K") +
  theme_bw()
```


```{r, echo = FALSE}
ss_k_pos + ws_k_pos +
  plot_annotation(title = "Simulation of K ranges on B/K ratio - Negative values filtered out")
```


### Price ratio vs Vulnerability test

```{r, echo = FALSE}
# vul_full <- 
#   output_test %>% 
#   filter(variables %in% c("N_w", "N_s")) %>% 
#   mutate(prod_ratio = (q_s/r_s) / (q_w/r_w)) %>% 
#   ggplot() +
#   geom_point(aes(x = price_ratio, y = prod_ratio, color = values)) +
#   scale_color_gradientn(name = "stock size", colors = RColorBrewer::brewer.pal(5, "YlOrRd")) +
#   labs(x = "Price ratio (p_s/p_w)",
#        y = "Vulnerability ratio (q_s/r_s)/(q_w/r_w)",
#        title = "All values") +
#   theme_bw()
```

```{r, echo = FALSE}
# vul_pos <- 
#   output_test %>% 
#   filter(variables %in% c("N_w", "N_s") & values >= 0) %>% 
#   mutate(prod_ratio = (q_s/r_s) / (q_w/r_w)) %>% 
#   ggplot() +
#   geom_point(aes(x = price_ratio, y = prod_ratio, color = values)) +
#   scale_color_gradientn(name = "stock size", colors = RColorBrewer::brewer.pal(5, "YlOrRd")) +
#   labs(x = "Price ratio (p_s/p_w)",
#        y = "Vulnerability ratio (q_s/r_s)/(q_w/r_w)",
#        title = "Only positive values") +
#   theme_bw()
```

```{r, echo = FALSE}
# vul_neg <- 
#   output_test %>% 
#   filter(variables %in% c("N_w", "N_s") & values <= 0) %>% 
#   mutate(prod_ratio = (q_s/r_s) / (q_w/r_w)) %>% 
#   ggplot() +
#   geom_point(aes(x = price_ratio, y = prod_ratio, color = values)) +
#   scale_color_gradientn(name = "stock size", colors = RColorBrewer::brewer.pal(5, "YlOrRd"),
#                         breaks = seq(-60, 0, 10)) +
#   labs(x = "Price ratio (p_s/p_w)",
#        y = "Vulnerability ratio (q_s/r_s)/(q_w/r_w)",
#        title = "Only negative values") +
#   theme_bw()
```


```{r, fig.height = 10, fig.width=9, echo = FALSE}
# (vul_neg + vul_pos) /
#   vul_full +
#   plot_annotation(title = "Simulation of the distribution of vulnerability and price ratios")
```

```{r, echo = FALSE}
vul_s <- 
  output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s") %>% 
  ggplot() +
  geom_point(aes(x = price_ratio, y = vuln_ratio, color = b_v_k)) +
  scale_color_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Price ratio",
       y = "Vulnerability ratio",
       title = "Strong stock",
       color = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
vul_w <- 
  output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w") %>% 
  ggplot() +
  geom_point(aes(x = price_ratio, y = vuln_ratio, color = b_v_k)) +
  scale_color_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0)) +
  labs(x = "Price ratio",
       y = "Vulnerability ratio",
       title = "Weak stock",
       color = "B/K") +
  theme_bw()
```

```{r, echo = FALSE, fig.height=9, fig.width=8}
vul_s + vul_w +
  plot_annotation(title = "Price vs vulnerability ratios for strong and weak stocks - All B/K values",
                  caption = "Price ratio = p_s / p_w \n Vulnerability ratio = (q_s/r_s) / (q_w/r_w)")
```

```{r, echo = FALSE}
vul_pos_s <- 
  output_test_updated %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s" & b_v_k >= 0) %>% 
  ggplot() +
  geom_point(aes(x = price_ratio, y = vuln_ratio, color = b_v_k)) +
  scale_color_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Price ratio",
       y = "Vulnerability ratio",
       title = "Strong stock",
       color = "B/K") +
  theme_bw()
```

```{r, echo = FALSE}
vul_pos_w <- 
  output_test_updated %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w" & b_v_k >= 0) %>% 
  ggplot() +
  geom_point(aes(x = price_ratio, y = vuln_ratio, color = b_v_k)) +
  scale_color_distiller(palette = "RdYlBu",
                       rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Price ratio",
       y = "Vulnerability ratio",
       title = "Weak stock",
       color = "B/K") +
  theme_bw()
```

```{r, echo = FALSE, fig.width=9, fig.height=6}
vul_pos_s + vul_pos_w +
  plot_annotation(title = "Price vs vulnerability ratios for strong and weak stocks - Positive B/K values",
                  caption = "Price ratio = p_s / p_w \n Vulnerability ratio = (q_s/r_s) / (q_w/r_w)")
```

- When transforming the negative values of B/K into zeros, we get the following plot:

```{r, echo = FALSE}
output_test_updated %>% 
  mutate(b_v_k = case_when(
    b_v_k < 0 ~ 0,
    TRUE ~ b_v_k
  )) %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w" & b_v_k >= 0) %>% 
  ggplot() +
  geom_point(aes(x = price_ratio, y = vuln_ratio, color = b_v_k),
             alpha = 0.2) +
  scale_color_paletteer_c("viridis::plasma",
                          rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Price ratio",
       y = "Vulnerability ratio",
       title = "Weak stock - values above 1 filtered out",
       color = "B/K") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title = element_text(size = 10, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
```


```{r, echo = FALSE}
test <- output_test_updated %>% 
  filter(q_s == 0.1 & q_w == 0.1) %>% 
  mutate(vuln_ratio = (q_s/r_s) / (q_w / r_w))

ws_test <- test %>% 
   mutate(b_v_k = case_when(
     b_v_k < 0 ~ 0,
     TRUE ~ b_v_k
   )) %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w" & b_v_k <= 1 & price_ratio <= 10) %>% 
  ggplot() +
  geom_point(aes(x = price_ratio, y = vuln_ratio, color = b_v_k),
             alpha = 0.2) +
  scale_color_paletteer_c("viridis::plasma",
                          rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  scale_x_continuous(breaks = seq(0, 10, 2),
                     limits = c(0, 10),
                     expand = c(0.01,0)) +
  labs(x = "Price ratio",
       y = "",
       title = "",
       color = "B/K") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title = element_text(size = 10, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
```

```{r, echo = FALSE}
ss_test <- 
  test %>% 
   mutate(b_v_k = case_when(
     b_v_k < 0 ~ 0,
     TRUE ~ b_v_k
   )) %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s" & b_v_k <= 1 & price_ratio <= 10) %>% 
  ggplot() +
  geom_point(aes(x = price_ratio, y = vuln_ratio, color = b_v_k),
             alpha = 0.2,
             show.legend = F) +
  scale_color_paletteer_c("viridis::plasma",
                          rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  scale_x_continuous(breaks = seq(0, 10, 2),
                     limits = c(0, 10),
                     expand = c(0.01,0)) +
  labs(x = "Price ratio",
       y = "Vulnerability ratio",
       title = "",
       color = "B/K") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title = element_text(size = 10, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
```

```{r, echo = FALSE, fig.height=5, fig.width=8}
ss_test + labs(tag = 'A') + ws_test + labs(tag = 'B') +
  plot_layout(guides = "collect")
#  plot_annotation(title = "Price vs vulnerability ratios for strong and weak stocks - B/K values above 1 filtered out")
```

```{r, echo = FALSE, include = FALSE}
test <- output_test_updated %>% 
  filter(q_s == 0.1 & q_w == 0.1) %>% 
  pivot_wider(names_from = "variables",
              values_from = "values") %>% 
  mutate(vuln_ratio_test = (q_s * e/ r_s * N_s) / (q_w * e/ r_w * N_w)) %>% 
  pivot_longer(cols = e:N_w,
               names_to = "variables",
               values_to = "values")

test %>% 
   mutate(b_v_k = case_when(
     b_v_k < 0 ~ 0,
     TRUE ~ b_v_k
   )) %>% 
  filter(variables == "N_s" & b_stocks == "b_values_s" & b_v_k <= 1) %>% 
  ggplot() +
  geom_point(aes(x = log1p(price_ratio), y = log1p(vuln_ratio), color = b_v_k),
             alpha = 0.2) +
  scale_color_paletteer_c("viridis::plasma",
                          rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Price ratio",
       y = "Vulnerability ratio",
       title = "Strong stock",
       color = "B/K") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title = element_text(size = 10, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
```

```{r, include = FALSE}
test %>% 
   mutate(b_v_k = case_when(
     b_v_k < 0 ~ 0,
     TRUE ~ b_v_k
   )) %>% 
  filter(variables == "N_w" & b_stocks == "b_values_w" & b_v_k <= 1) %>% 
  ggplot() +
  geom_point(aes(x = log1p(price_ratio), y = log1p(vuln_ratio), color = b_v_k),
             alpha = 0.2) +
  scale_color_paletteer_c("viridis::plasma",
                          rescaler = ~ scales::rescale_mid(.x, mid = 0.5)) +
  labs(x = "Price ratio",
       y = "Vulnerability ratio",
       title = "Weak stock",
       color = "B/K") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title = element_text(size = 10, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
```


```{r, echo = FALSE}
q_neg <- 
  output_test_updated %>% 
  filter(values < 0) %>% 
  ggplot() +
  geom_raster(aes(x = q_w, y = q_s, fill = values)) +
  facet_wrap(~ variables) +
#  scale_fill_continuous(breaks = seq(-10, 0, 2)) +
  labs(title = "Negative values") +
  theme_bw()
```

```{r, echo = FALSE}
q_pos <-
  output_test_updated %>% 
  filter(values >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = q_w, y = q_s, fill = values)) +
  facet_wrap(~ variables) +
  scale_fill_continuous(breaks = seq(0, 25, 5)) +
  labs(title = "Positive values") +
  theme_bw()
```


```{r, fig.width=9, echo = FALSE}
# (q_neg + q_pos) +
#   plot_annotation(title = "Catchability ranges")
```



```{r, echo = FALSE}
r_neg <- 
  output_test_updated %>% 
  filter(values <= 0) %>% 
  ggplot() +
  geom_raster(aes(x = r_w, y = r_s, fill = values)) +
  facet_wrap(~ variables) +
  labs(title = "Negative values for r scenarios") +
  theme_bw()
```

```{r, echo = FALSE}
r_pos <- 
  output_test_updated %>% 
  filter(values >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = r_w, y = r_s, fill = values)) +
  facet_wrap(~ variables) +
  scale_fill_continuous(breaks = seq(0, 25, 5)) +
  labs(title = "Positive values for r scenarios") +
  theme_bw()
```

```{r, fig.width=8, echo = FALSE}
# r_neg + r_pos +
#   plot_annotation(title = "Range of values for r scenarios")
```


```{r, echo = FALSE}
k_neg <-
  output_test_updated %>% 
  filter(values <= 0) %>% 
  ggplot() +
  geom_raster(aes(x = k_w, y = k_s, fill = values)) +
  facet_wrap(~ variables) +
  labs(title = "Negative values for K ranges") +
  theme_bw()
```

```{r, echo = FALSE}
k_pos <-
  output_test_updated %>% 
  filter(values >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = k_w, y = k_s, fill = values)) +
  facet_wrap(~ variables) + 
  scale_fill_continuous(breaks = seq(0, 25, 5)) +
  labs(title = "Positive values for K ranges") +
  theme_bw()
```

```{r, fig.width=8, echo = FALSE}
# k_neg + k_pos +
#   plot_annotation(title = "Range of values for K scenarios")
```



```{r, echo = FALSE}
price_neg <-
  output_test_updated %>% 
  filter(values <= 0) %>% 
  ggplot() +
  geom_raster(aes(x = p_w, y = p_s, fill = values)) +
  facet_wrap(~ variables) +
  scale_x_continuous(breaks = seq(0, 10, 2)) +
  labs(title = "Negative values for the range of prices") +
  theme_bw()
```

```{r, echo = FALSE}
pos_price <- 
  output_test_updated %>% 
  filter(values >= 0) %>% 
  ggplot() +
  geom_raster(aes(x = p_w, y = p_s, fill = values)) +
  facet_wrap(~ variables) +
  scale_fill_continuous(breaks = seq(0, 25, 5)) +
  labs(title = "Positive values for the range of prices") +
  theme_bw()
```

```{r, fig.width=8, echo = FALSE}
# price_neg + pos_price +
#   plot_annotation(title = "Values for the range of prices")
```


## Time series equations

$$
\begin{align}
\frac{d N_s}{dt} &= N_S  (r_s  (1 - (\frac{N_S}{K_s})) - q_s E) \\
\newline
\frac{d N_w}{dt} &= N_W  (r_w  (1 - (\frac{N_W}{K_w})) - q_w E) \\
\newline
\frac{d E}{dt} &= \alpha  E  (p_s  q_s  N_S + p_w q_w N_W - c)
\newline
\frac{d C_s}{dt} &= q N_s E
\newline
\frac{d C_w}{dt} &= q N_w E
\newline
\frac{d CPUE_s}{dt} &= \frac{C_s} {E}
\newline
\frac{d CPUE_w}{dt} &= \frac{C_w} {E}
\newline
\frac{d \pi_s}{dt} &= C_s p_s - C_s  c
\newline
\frac{d \pi_w}{dt} &= C_w p_W - C_w  c
\newline
\frac{d \pi}{dt} &= C_s  p_s + C_w  p_w - (C_s + C_w) * c
\end{align}
$$


where $q_s$ and $q_w$ are the catchability of the strong and the weak stock, respectively; $r_s$ and $r_w$ are the intrinsic growth rates of the strong and weak stocks, respectively; $p_s$ and $p_w$ are the prices of the strong and weak stocks, respectively; $k_s$ and $k_w$ are the carrying capacities of the strong and weak stocks, respectively; $c$ is the fishing cost, and $\alpha$ is a constant controling for the speed at which effort changes following price changes.

### Scenarios for a range of price ratios

```{r scenario 1 price ratio 10, echo = FALSE}
# set up the parameter space
q_s <- 0.1
q_w <- 0.1
k_s <- 4
k_w <- 2
r_s <- 0.8
r_w <- 0.45
p_s1 <- 1
p_w1 <- 0.1
alpha <- 1
c <- 0.05

# Initial values for the variables
N_w <- k_w

N_s <- k_s

E <- 0.1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu1 <- NaN*tset; N_w_simu1[1] <- N_w

N_s_simu1 <- NaN*tset; N_s_simu1[1] <- N_s

#N_w_test_1 <- NaN*tset; N_w_test_1[1] <- N_w

#N_s_test_1 <- NaN*tset; N_s_test_1[1] <- N_s

E_simu1 <- NaN*tset; E_simu1[1] <- E

#E_test1 <- NaN*tset; E_test1[1] <- E

C_s_simu1 <- NaN*tset; C_s_simu1[1] <- 1

C_w_simu1 <- NaN*tset; C_w_simu1[1] <- 1

cpue_s_simu1 <- NaN*tset; cpue_s_simu1[1] <- 1

cpue_w_simu1 <- NaN*tset; cpue_w_simu1[1] <- 1

Pi_sum_simu1 <- NaN*tset; Pi_sum_simu1[1] <- 2

Pi_s_simu1 <- NaN*tset; Pi_s_simu1[1] <- 1

Pi_w_simu1 <- NaN*tset; Pi_w_simu1[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w1 <- N_w_simu1[i-1]
  N_s1 <- N_s_simu1[i-1]
  #N_wt1 <- N_w_test_1[i-1]
  #N_st1 <- N_s_test_1[i-1]
  E1 <- E_simu1[i-1]
  #E_t1 <- E_test1[i-1]
  C_s1 <- C_s_simu1[i-1]
  C_w1 <- C_w_simu1[i-1]
  cpue_s1 <- cpue_s_simu1[i-1]
  cpue_w1 <- cpue_w_simu1[i-1]
  pi1 <- Pi_sum_simu1[i-1]
  pi_s1 <- Pi_s_simu1[i-1]
  pi_w1 <- Pi_w_simu1[i-1]
    
  # Calculate change in variable size at each time step
  dN_s1 <- (N_s1 * (r_s * (1 - (N_s1/k_s)) - q_s * E1)) * dt
  dN_w1 <- (N_w1 * (r_w * (1 - (N_w1/k_w)) - q_w * E1)) * dt
  #dN_st1 <- (N_st1 * (r_s * (1 - (N_st1/k_s)) - q_s * E_t1)) * dt
  #dN_wt1 <- (N_wt1 * (r_w * (1 - (N_wt1/k_w)) - q_w * E_t1)) * dt
  dE1 <- (alpha * E1 * (p_s1 * q_s * N_s1 + p_w1 * q_w * N_w1 - c)) * dt
  #dE_test1 <- ((p_s1 * q_s1 * N_st1 + p_w1 * q_w1 * N_wt1) - c) * dt
  dC_s1 <- (q_s * N_s1 * E1) * dt
  dC_w1 <- (q_w * N_w1 * E1) * dt
  dcpue_s1 <- (C_s1 / E1) * dt
  dcpue_w1 <- (C_w1 / E1) * dt
  dPi_s1 <- (C_s1 * p_s1 - C_s1 * c) * dt
  dPi_w1 <- (C_w1 * p_w1 - C_w1 * c) * dt
  dPi1 <- (C_s1 * p_s1 + C_w1 * p_w1 - ((C_s1 + C_w1) * c)) * dt
  # calculate total variable size and store in holding vectors
  
  N_w_simu1[i] <- N_w1 + dN_w1
  N_s_simu1[i] <- N_s1 + dN_s1
  #N_w_test_1[i] <- N_wt1 + dN_wt1
  #N_s_test_1[i] <- N_st1 + dN_st1
  E_simu1[i] <- E1 + dE1
  #E_test1[i] <- E_t1 + dE_test1
  C_s_simu1[i] <- C_s1 + dC_s1
  C_w_simu1[i] <- C_w1 + dC_w1
  cpue_s_simu1[i] <- cpue_s1 + dcpue_s1
  cpue_w_simu1[i] <- cpue_w1 + dcpue_w1
  Pi_sum_simu1[i] <- pi1 + dPi1
  Pi_s_simu1[i] <- pi_s1 + dPi_s1
  Pi_w_simu1[i] <- pi_w1 + dPi_w1
  
}
  

```



```{r scenario 2 price ratio 5, echo = FALSE}
p_s2 <- 1
p_w2 <- 0.2
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu2 <- NaN*tset; N_w_simu2[1] <- N_w

N_s_simu2 <- NaN*tset; N_s_simu2[1] <- N_s

#N_w_test_2 <- NaN*tset; N_w_test_2[1] <- N_w

#N_s_test_2 <- NaN*tset; N_s_test_2[1] <- N_s

E_simu2 <- NaN*tset; E_simu2[1] <- E

#E_test2 <- NaN*tset; E_test2[1] <- E

C_s_simu2 <- NaN*tset; C_s_simu2[1] <- 1

C_w_simu2 <- NaN*tset; C_w_simu2[1] <- 1

cpue_s_simu2 <- NaN*tset; cpue_s_simu2[1] <- 1

cpue_w_simu2 <- NaN*tset; cpue_w_simu2[1] <- 1

Pi_sum_simu2 <- NaN*tset; Pi_sum_simu2[1] <- 2

Pi_s_simu2 <- NaN*tset; Pi_s_simu2[1] <- 1

Pi_w_simu2 <- NaN*tset; Pi_w_simu2[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w2 <- N_w_simu2[i-1]
  N_s2 <- N_s_simu2[i-1]
  #N_wt2 <- N_w_test_2[i-1]
  #N_st2 <- N_s_test_2[i-1]
  E2 <- E_simu2[i-1]
  #E_t2 <- E_test2[i-1]
  C_s2 <- C_s_simu2[i-1]
  C_w2 <- C_w_simu2[i-1]
  cpue_s2 <- cpue_s_simu2[i-1]
  cpue_w2 <- cpue_w_simu2[i-1]
  pi2 <- Pi_sum_simu2[i-1]
  pi_s2 <- Pi_s_simu2[i-1]
  pi_w2 <- Pi_w_simu2[i-1]

  # Calculate change in variable size at each time step
  dN_s2 <- (N_s2 * (r_s * (1 - (N_s2/k_s)) - q_s * E2)) * dt
  dN_w2 <- (N_w2 * (r_w * (1 - (N_w2/k_w)) - q_w * E2)) * dt
  #dN_st2 <- (N_st2 * (r_s2 * (1 - (N_st2/k_s2)) - q_s2 * E_t2)) * dt
  #dN_wt2 <- (N_wt2 * (r_w2 * (1 - (N_wt2/k_w2)) - q_w2 * E_t2)) * dt
  dE2 <- (alpha * E2 * (p_s2 * q_s * N_s2 + p_w2 * q_w * N_w2 - c)) * dt
  #dE_test2 <- ((p_s2 * q_s2 * N_st2 + p_w2 * q_w2 * N_wt2) - c) * dt
  dC_s2 <- (q_s * N_s2 * E2) * dt
  dC_w2 <- (q_w * N_w2 * E2) * dt
  dcpue_s2 <- (C_s2 / E2) * dt
  dcpue_w2 <- (C_w2 / E2) * dt
  dPi_s2 <- (C_s2 * p_s2 - C_s2 * c) * dt
  dPi_w2 <- (C_w2 * p_w2 - C_w2 * c) * dt
  dPi2 <- (C_s2 * p_s2 + C_w2 * p_w2 - ((C_s2 + C_w2) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu2[i] <- N_w2 + dN_w2
  N_s_simu2[i] <- N_s2 + dN_s2
  #N_w_test_2[i] <- N_wt2 + dN_wt2
  #N_s_test_2[i] <- N_st2 + dN_st2
  E_simu2[i] <- E2 + dE2
  #E_test2[i] <- E_t2 + dE_test2
  C_s_simu2[i] <- C_s2 + dC_s2
  C_w_simu2[i] <- C_w2 + dC_w2
  cpue_s_simu2[i] <- cpue_s2 + dcpue_s2
  cpue_w_simu2[i] <- cpue_w2 + dcpue_w2
  Pi_sum_simu2[i] <- pi2 + dPi2
  Pi_s_simu2[i] <- pi_s2 + dPi_s2
  Pi_w_simu2[i] <- pi_w2 + dPi_w2
}
```


```{r scenario 3 price ratio 2.5, echo = FALSE}
# set up the parameter space
p_s3 <- 1
p_w3 <- 0.4
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu3 <- NaN*tset; N_w_simu3[1] <- N_w

N_s_simu3 <- NaN*tset; N_s_simu3[1] <- N_s

#N_w_test_3 <- NaN*tset; N_w_test_3[1] <- N_w

#N_s_test_3 <- NaN*tset; N_s_test_3[1] <- N_s

E_simu3 <- NaN*tset; E_simu3[1] <- E

#E_test3 <- NaN*tset; E_test3[1] <- E

C_s_simu3 <- NaN*tset; C_s_simu3[1] <- 1

C_w_simu3 <- NaN*tset; C_w_simu3[1] <- 1

cpue_s_simu3 <- NaN*tset; cpue_s_simu3[1] <- 1

cpue_w_simu3 <- NaN*tset; cpue_w_simu3[1] <- 1

Pi_sum_simu3 <- NaN*tset; Pi_sum_simu3[1] <- 2

Pi_s_simu3 <- NaN*tset; Pi_s_simu3[1] <- 1

Pi_w_simu3 <- NaN*tset; Pi_w_simu3[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w3 <- N_w_simu3[i-1]
  N_s3 <- N_s_simu3[i-1]
  #N_wt3 <- N_w_test_3[i-1]
  #N_st3 <- N_s_test_3[i-1]
  E3 <- E_simu3[i-1]
  #E_t3 <- E_test3[i-1]
  C_s3 <- C_s_simu3[i-1]
  C_w3 <- C_w_simu3[i-1]
  cpue_s3 <- cpue_s_simu3[i-1]
  cpue_w3 <- cpue_w_simu3[i-1]
  pi3 <- Pi_sum_simu3[i-1]
  pi_s3 <- Pi_s_simu3[i-1]
  pi_w3 <- Pi_w_simu3[i-1]

  # Calculate change in variable size at each time step
  dN_s3 <- (N_s3 * (r_s * (1 - (N_s3/k_s)) - q_s * E3)) * dt
  dN_w3 <- (N_w3 * (r_w * (1 - (N_w3/k_w)) - q_w * E3)) * dt
  #dN_st3 <- (N_st3 * (r_s3 * (1 - (N_st3/k_s3)) - q_s3 * E_t3)) * dt
  #dN_wt3 <- (N_wt3 * (r_w3 * (1 - (N_wt3/k_w3)) - q_w3 * E_t3)) * dt
  dE3 <- (alpha * E3 * (p_s3 * q_s * N_s3 + p_w3 * q_w * N_w3 - c)) * dt
  #dE_test3 <- ((p_s3 * q_s3 * N_st3 + p_w3 * q_w3 * N_wt3) - c) * dt
  dC_s3 <- (q_s * N_s3 * E3) * dt
  dC_w3 <- (q_w * N_w3 * E3) * dt
  dcpue_s3 <- (C_s3 / E3) * dt
  dcpue_w3 <- (C_w3 / E3) * dt
  dPi_s3 <- (C_s3 * p_s3 - C_s3 * c) * dt
  dPi_w3 <- (C_w3 * p_w3 - C_w3 * c) * dt
  dPi3 <- (C_s3 * p_s3 + C_w3 * p_w3 - ((C_s3 + C_w3) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu3[i] <- N_w3 + dN_w3
  N_s_simu3[i] <- N_s3 + dN_s3
  #N_w_test_3[i] <- N_wt3 + dN_wt3
  #N_s_test_3[i] <- N_st3 + dN_st3
  E_simu3[i] <- E3 + dE3
  #E_test3[i] <- E_t3 + dE_test3
  C_s_simu3[i] <- C_s3 + dC_s3
  C_w_simu3[i] <- C_w3 + dC_w3
  cpue_s_simu3[i] <- cpue_s3 + dcpue_s3
  cpue_w_simu3[i] <- cpue_w3 + dcpue_w3
  Pi_sum_simu3[i] <- pi3 + dPi3
  Pi_s_simu3[i] <- pi_s3 + dPi_s3
  Pi_w_simu3[i] <- pi_w3 + dPi_w3

}
```


```{r scenario 4 price ratio 1, echo = FALSE}
# set up the parameter space
p_s4 <- 1
p_w4 <- 1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu4 <- NaN*tset; N_w_simu4[1] <- N_w

N_s_simu4 <- NaN*tset; N_s_simu4[1] <- N_s

#N_w_test_4 <- NaN*tset; N_w_test_4[1] <- N_w

#N_s_test_4 <- NaN*tset; N_s_test_4[1] <- N_s

E_simu4 <- NaN*tset; E_simu4[1] <- E

#E_test4 <- NaN*tset; E_test4[1] <- E

C_s_simu4 <- NaN*tset; C_s_simu4[1] <- 1

C_w_simu4 <- NaN*tset; C_w_simu4[1] <- 1

cpue_s_simu4 <- NaN*tset; cpue_s_simu4[1] <- 1

cpue_w_simu4 <- NaN*tset; cpue_w_simu4[1] <- 1

Pi_sum_simu4 <- NaN*tset; Pi_sum_simu4[1] <- 2

Pi_s_simu4 <- NaN*tset; Pi_s_simu4[1] <- 1

Pi_w_simu4 <- NaN*tset; Pi_w_simu4[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w4 <- N_w_simu4[i-1]
  N_s4 <- N_s_simu4[i-1]
  #N_wt4 <- N_w_test_4[i-1]
  #N_st4 <- N_s_test_4[i-1]
  E4 <- E_simu4[i-1]
  #E_t4 <- E_test4[i-1]
  C_s4 <- C_s_simu4[i-1]
  C_w4 <- C_w_simu4[i-1]
  cpue_s4 <- cpue_s_simu4[i-1]
  cpue_w4 <- cpue_w_simu4[i-1]
  pi4 <- Pi_sum_simu4[i-1]
  pi_s4 <- Pi_s_simu4[i-1]
  pi_w4 <- Pi_w_simu4[i-1]

  # Calculate change in variable size at each time step
  dN_s4 <- (N_s4 * (r_s * (1 - (N_s4/k_s)) - q_s * E4)) * dt
  dN_w4 <- (N_w4 * (r_w * (1 - (N_w4/k_w)) - q_w * E4)) * dt
  #dN_st4 <- (N_st4 * (r_s4 * (1 - (N_st4/k_s4)) - q_s4 * E_t4)) * dt
  #dN_wt4 <- (N_wt4 * (r_w4 * (1 - (N_wt4/k_w4)) - q_w4 * E_t4)) * dt
  dE4 <- (alpha * E4 * (p_s4 * q_s * N_s4 + p_w4 * q_w * N_w4 - c)) * dt
  #dE_test4 <- ((p_s4 * q_s4 * N_st4 + p_w4 * q_w4 * N_wt4) - c) * dt
  dC_s4 <- (q_s * N_s4 * E4) * dt
  dC_w4 <- (q_w * N_w4 * E4) * dt
  dcpue_s4 <- (C_s4 / E4) * dt
  dcpue_w4 <- (C_w4 / E4) * dt
  dPi_s4 <- (C_s4 * p_s4 - C_s4 * c) * dt
  dPi_w4 <- (C_w4 * p_w4 - C_w4 * c) * dt
  dPi4 <- (C_s4 * p_s4 + C_w4 * p_w4 - ((C_s4 + C_w4) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu4[i] <- N_w4 + dN_w4
  N_s_simu4[i] <- N_s4 + dN_s4
  #N_w_test_4[i] <- N_wt4 + dN_wt4
  #N_s_test_4[i] <- N_st4 + dN_st4
  E_simu4[i] <- E4 + dE4
  #E_test4[i] <- E_t4 + dE_test4
  C_s_simu4[i] <- C_s4 + dC_s4
  C_w_simu4[i] <- C_w4 + dC_w4
  cpue_s_simu4[i] <- cpue_s4 + dcpue_s4
  cpue_w_simu4[i] <- cpue_w4 + dcpue_w4
  Pi_sum_simu4[i] <- pi4 + dPi4
  Pi_s_simu4[i] <- pi_s4 + dPi_s4
  Pi_w_simu4[i] <- pi_w4 + dPi_w4
  
}
```


```{r scenario 5 price ratio 0.75, echo = FALSE}
# set up the parameter space
p_s5 <- 0.75
p_w5 <- 1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu5 <- NaN*tset; N_w_simu5[1] <- N_w

N_s_simu5 <- NaN*tset; N_s_simu5[1] <- N_s

#N_w_test_5 <- NaN*tset; N_w_test_5[1] <- N_w

#N_s_test_5 <- NaN*tset; N_s_test_5[1] <- N_s

E_simu5 <- NaN*tset; E_simu5[1] <- E

#E_test5 <- NaN*tset; E_test5[1] <- E

C_s_simu5 <- NaN*tset; C_s_simu5[1] <- 1

C_w_simu5 <- NaN*tset; C_w_simu5[1] <- 1

cpue_s_simu5 <- NaN*tset; cpue_s_simu5[1] <- 1

cpue_w_simu5 <- NaN*tset; cpue_w_simu5[1] <- 1

Pi_sum_simu5 <- NaN*tset; Pi_sum_simu5[1] <- 2

Pi_s_simu5 <- NaN*tset; Pi_s_simu5[1] <- 1

Pi_w_simu5 <- NaN*tset; Pi_w_simu5[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w5 <- N_w_simu5[i-1]
  N_s5 <- N_s_simu5[i-1]
  #N_wt5 <- N_w_test_5[i-1]
  #N_st5 <- N_s_test_5[i-1]
  E5 <- E_simu5[i-1]
  #E_t5 <- E_test5[i-1]
  C_s5 <- C_s_simu5[i-1]
  C_w5 <- C_w_simu5[i-1]
  cpue_s5 <- cpue_s_simu5[i-1]
  cpue_w5 <- cpue_w_simu5[i-1]
  pi5 <- Pi_sum_simu5[i-1]
  pi_s5 <- Pi_s_simu5[i-1]
  pi_w5 <- Pi_w_simu5[i-1]

  # Calculate change in variable size at each time step
  dN_s5 <- (N_s5 * (r_s * (1 - (N_s5/k_s)) - q_s * E5)) * dt
  dN_w5 <- (N_w5 * (r_w * (1 - (N_w5/k_w)) - q_w * E5)) * dt
  #dN_st5 <- (N_st5 * (r_s5 * (1 - (N_st5/k_s5)) - q_s5 * E_t5)) * dt
  #dN_wt5 <- (N_wt5 * (r_w5 * (1 - (N_wt5/k_w5)) - q_w5 * E_t5)) * dt
  dE5 <- (alpha * E5 * (p_s5 * q_s * N_s5 + p_w5 * q_w * N_w5 - c)) * dt
  #dE_test5 <- ((p_s5 * q_s5 * N_st5 + p_w5 * q_w5 * N_wt5) - c) * dt
  dC_s5 <- (q_s * N_s5 * E5) * dt
  dC_w5 <- (q_w * N_w5 * E5) * dt
  dcpue_s5 <- (C_s5 / E5) * dt
  dcpue_w5 <- (C_w5 / E5) * dt
  dPi_s5 <- (C_s5 * p_s5 - C_s5 * c) * dt
  dPi_w5 <- (C_w5 * p_w5 - C_w5 * c) * dt
  dPi5 <- (C_s5 * p_s5 + C_w5 * p_w5 - ((C_s5 + C_w5) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu5[i] <- N_w5 + dN_w5
  N_s_simu5[i] <- N_s5 + dN_s5
  #N_w_test_5[i] <- N_wt5 + dN_wt5
  #N_s_test_5[i] <- N_st5 + dN_st5
  E_simu5[i] <- E5 + dE5
  #E_test5[i] <- E_t5 + dE_test5
  C_s_simu5[i] <- C_s5 + dC_s5
  C_w_simu5[i] <- C_w5 + dC_w5
  cpue_s_simu5[i] <- cpue_s5 + dcpue_s5
  cpue_w_simu5[i] <- cpue_w5 + dcpue_w5
  Pi_sum_simu5[i] <- pi5 + dPi5
  Pi_s_simu5[i] <- pi_s5 + dPi_s5
  Pi_w_simu5[i] <- pi_w5 + dPi_w5  
}
```



```{r scenario 6 price ratio 0.5, echo = FALSE}
p_s6 <- 0.5
p_w6 <- 1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu6 <- NaN*tset; N_w_simu6[1] <- N_w

N_s_simu6 <- NaN*tset; N_s_simu6[1] <- N_s

#N_w_test_6 <- NaN*tset; N_w_test_6[1] <- N_w

#N_s_test_6 <- NaN*tset; N_s_test_6[1] <- N_s

E_simu6 <- NaN*tset; E_simu6[1] <- E

#E_test6 <- NaN*tset; E_test6[1] <- E

C_s_simu6 <- NaN*tset; C_s_simu6[1] <- 1

C_w_simu6 <- NaN*tset; C_w_simu6[1] <- 1

cpue_s_simu6 <- NaN*tset; cpue_s_simu6[1] <- 1

cpue_w_simu6 <- NaN*tset; cpue_w_simu6[1] <- 1

Pi_sum_simu6 <- NaN*tset; Pi_sum_simu6[1] <- 2

Pi_s_simu6 <- NaN*tset; Pi_s_simu6[1] <- 1

Pi_w_simu6 <- NaN*tset; Pi_w_simu6[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w6 <- N_w_simu6[i-1]
  N_s6 <- N_s_simu6[i-1]
  #N_wt6 <- N_w_test_6[i-1]
  #N_st6 <- N_s_test_6[i-1]
  E6 <- E_simu6[i-1]
  #E_t6 <- E_test6[i-1]
  C_s6 <- C_s_simu6[i-1]
  C_w6 <- C_w_simu6[i-1]
  cpue_s6 <- cpue_s_simu6[i-1]
  cpue_w6 <- cpue_w_simu6[i-1]
  pi6 <- Pi_sum_simu6[i-1]
  pi_s6 <- Pi_s_simu6[i-1]
  pi_w6 <- Pi_w_simu6[i-1]

  # Calculate change in variable size at each time step
  dN_s6 <- (N_s6 * (r_s * (1 - (N_s6/k_s)) - q_s * E6)) * dt
  dN_w6 <- (N_w6 * (r_w * (1 - (N_w6/k_w)) - q_w * E6)) * dt
  #dN_st6 <- (N_st6 * (r_s6 * (1 - (N_st6/k_s6)) - q_s6 * E_t6)) * dt
  #dN_wt6 <- (N_wt6 * (r_w6 * (1 - (N_wt6/k_w6)) - q_w6 * E_t6)) * dt
  dE6 <- (alpha * E6 * (p_s6 * q_s * N_s6 + p_w6 * q_w * N_w6 - c)) * dt
  #dE_test6 <- ((p_s6 * q_s6 * N_st6 + p_w6 * q_w6 * N_wt6) - c) * dt
  dC_s6 <- (q_s * N_s6 * E6) * dt
  dC_w6 <- (q_w * N_w6 * E6) * dt
  dcpue_s6 <- (C_s6 / E6) * dt
  dcpue_w6 <- (C_w6 / E6) * dt
  dPi_s6 <- (C_s6 * p_s6 - C_s6 * c) * dt
  dPi_w6 <- (C_w6 * p_w6 - C_w6 * c) * dt
  dPi6 <- (C_s6 * p_s6 + C_w6 * p_w6 - ((C_s6 + C_w6) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  N_w_simu6[i] <- N_w6 + dN_w6
  N_s_simu6[i] <- N_s6 + dN_s6
  #N_w_test_6[i] <- N_wt6 + dN_wt6
  #N_s_test_6[i] <- N_st6 + dN_st6
  E_simu6[i] <- E6 + dE6
  #E_test6[i] <- E_t6 + dE_test6
  C_s_simu6[i] <- C_s6 + dC_s6
  C_w_simu6[i] <- C_w6 + dC_w6
  cpue_s_simu6[i] <- cpue_s6 + dcpue_s6
  cpue_w_simu6[i] <- cpue_w6 + dcpue_w6
  Pi_sum_simu6[i] <- pi6 + dPi6
  Pi_s_simu6[i] <- pi_s6 + dPi_s6
  Pi_w_simu6[i] <- pi_w6 + dPi_w6  
  
}
```


```{r, echo = FALSE, include = FALSE}
plot(x = tset, y = N_s_simu6,
     type = "l",
     col = "blue",
     las = 1,
     lwd = 2,
     ylim = c(0, 20),
     xlab = "Time", ylab = "Variable size")
lines(x = tset, y = N_w_simu6,
      type = "l", col = "orange")
lines(x = tset, y = E_simu6,
      type = "l", col = "green")
title(main = "Sixth simulation - Price ratio = 0.5",
      sub = "Params: q_s = 0.1, q_w = 0.1, r_s = 0.75, r_w = 0.25, k_s = 4, k_w = 2, p_s = 2.5, p_w = 5")
legend(x = 80, y = 20,
       lwd = 2,
       legend = c("Ns", "Nw", "E"),
       col = c("blue", "orange", "green"))
```



```{r scenario 7 price ratio 0.25, echo = FALSE}
p_s7 <- 0.25
p_w7 <- 1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu7 <- NaN*tset; N_w_simu7[1] <- N_w

N_s_simu7 <- NaN*tset; N_s_simu7[1] <- N_s

#N_w_test_7 <- NaN*tset; N_w_test_7[1] <- N_w

#N_s_test_7 <- NaN*tset; N_s_test_7[1] <- N_s

E_simu7 <- NaN*tset; E_simu7[1] <- E

#E_test7 <- NaN*tset; E_test7[1] <- E

C_s_simu7 <- NaN*tset; C_s_simu7[1] <- 1

C_w_simu7 <- NaN*tset; C_w_simu7[1] <- 1

cpue_s_simu7 <- NaN*tset; cpue_s_simu7[1] <- 1

cpue_w_simu7 <- NaN*tset; cpue_w_simu7[1] <- 1

Pi_sum_simu7 <- NaN*tset; Pi_sum_simu7[1] <- 2

Pi_s_simu7 <- NaN*tset; Pi_s_simu7[1] <- 1

Pi_w_simu7 <- NaN*tset; Pi_w_simu7[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w7 <- N_w_simu7[i-1]
  N_s7 <- N_s_simu7[i-1]
  #N_wt7 <- N_w_test_7[i-1]
  #N_st7 <- N_s_test_7[i-1]
  E7 <- E_simu7[i-1]
  #E_t7 <- E_test7[i-1]
  C_s7 <- C_s_simu7[i-1]
  C_w7 <- C_w_simu7[i-1]
  cpue_s7 <- cpue_s_simu7[i-1]
  cpue_w7 <- cpue_w_simu7[i-1]
  pi7 <- Pi_sum_simu7[i-1]
  pi_s7 <- Pi_s_simu7[i-1]
  pi_w7 <- Pi_w_simu7[i-1]

  # Calculate change in variable size at each time step
  dN_s7 <- (N_s7 * (r_s * (1 - (N_s7/k_s)) - q_s * E7)) * dt
  dN_w7 <- (N_w7 * (r_w * (1 - (N_w7/k_w)) - q_w * E7)) * dt
  #dN_st7 <- (N_st7 * (r_s7 * (1 - (N_st7/k_s7)) - q_s7 * E_t7)) * dt
  #dN_wt7 <- (N_wt7 * (r_w7 * (1 - (N_wt7/k_w7)) - q_w7 * E_t7)) * dt
  dE7 <- (alpha * E7 * (p_s7 * q_s * N_s7 + p_w7 * q_w * N_w7 - c)) * dt
  #dE_test7 <- ((p_s7 * q_s7 * N_st7 + p_w7 * q_w7 * N_wt7) - c) * dt
  dC_s7 <- (q_s * N_s7 * E7) * dt
  dC_w7 <- (q_w * N_w7 * E7) * dt
  dcpue_s7 <- (C_s7 / E7) * dt
  dcpue_w7 <- (C_w7 / E7) * dt
  dPi_s7 <- (C_s7 * p_s7 - C_s7 * c) * dt
  dPi_w7 <- (C_w7 * p_w7 - C_w7 * c) * dt
  dPi7 <- (C_s7 * p_s7 + C_w7 * p_w7 - ((C_s7 + C_w7) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu7[i] <- N_w7 + dN_w7
  N_s_simu7[i] <- N_s7 + dN_s7
  #N_w_test_7[i] <- N_wt7 + dN_wt7
  #N_s_test_7[i] <- N_st7 + dN_st7
  E_simu7[i] <- E7 + dE7
  #E_test7[i] <- E_t7 + dE_test7
  C_s_simu7[i] <- C_s7 + dC_s7
  C_w_simu7[i] <- C_w7 + dC_w7
  cpue_s_simu7[i] <- cpue_s7 + dcpue_s7
  cpue_w_simu7[i] <- cpue_w7 + dcpue_w7
  Pi_sum_simu7[i] <- pi7 + dPi7
  Pi_s_simu7[i] <- pi_s7 + dPi_s7
  Pi_w_simu7[i] <- pi_w7 + dPi_w7  
  
}
```


```{r scenario 8 price ratio 0.25, echo = FALSE}
# set up the parameter space
p_s8 <- 0.1
p_w8 <- 1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu8 <- NaN*tset; N_w_simu8[1] <- N_w

N_s_simu8 <- NaN*tset; N_s_simu8[1] <- N_s

#N_w_test_8 <- NaN*tset; N_w_test_8[1] <- N_w

#N_s_test_8 <- NaN*tset; N_s_test_8[1] <- N_s

E_simu8 <- NaN*tset; E_simu8[1] <- E

#E_test8 <- NaN*tset; E_test8[1] <- E

C_s_simu8 <- NaN*tset; C_s_simu8[1] <- 1

C_w_simu8 <- NaN*tset; C_w_simu8[1] <- 1

cpue_s_simu8 <- NaN*tset; cpue_s_simu8[1] <- 1

cpue_w_simu8 <- NaN*tset; cpue_w_simu8[1] <- 1

Pi_sum_simu8 <- NaN*tset; Pi_sum_simu8[1] <- 2

Pi_s_simu8 <- NaN*tset; Pi_s_simu8[1] <- 1

Pi_w_simu8 <- NaN*tset; Pi_w_simu8[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w8 <- N_w_simu8[i-1]
  N_s8 <- N_s_simu8[i-1]
  #N_wt8 <- N_w_test_8[i-1]
  #N_st8 <- N_s_test_8[i-1]
  E8 <- E_simu8[i-1]
  #E_t8 <- E_test8[i-1]
  C_s8 <- C_s_simu8[i-1]
  C_w8 <- C_w_simu8[i-1]
  cpue_s8 <- cpue_s_simu8[i-1]
  cpue_w8 <- cpue_w_simu8[i-1]
  pi8 <- Pi_sum_simu8[i-1]
  pi_s8 <- Pi_s_simu8[i-1]
  pi_w8 <- Pi_w_simu8[i-1]

  # Calculate change in variable size at each time step
  dN_s8 <- (N_s8 * (r_s * (1 - (N_s8/k_s)) - q_s * E8)) * dt
  dN_w8 <- (N_w8 * (r_w * (1 - (N_w8/k_w)) - q_w * E8)) * dt
  #dN_st8 <- (N_st8 * (r_s8 * (1 - (N_st8/k_s8)) - q_s8 * E_t8)) * dt
  #dN_wt8 <- (N_wt8 * (r_w8 * (1 - (N_wt8/k_w8)) - q_w8 * E_t8)) * dt
  dE8 <- (alpha * E8 * (p_s8 * q_s * N_s8 + p_w8 * q_w * N_w8 - c)) * dt
  #dE_test8 <- ((p_s8 * q_s8 * N_st8 + p_w8 * q_w8 * N_wt8) - c) * dt
  dC_s8 <- (q_s * N_s8 * E8) * dt
  dC_w8 <- (q_w * N_w8 * E8) * dt
  dcpue_s8 <- (C_s8 / E8) * dt
  dcpue_w8 <- (C_w8 / E8) * dt
  dPi_s8 <- (C_s8 * p_s8 - C_s8 * c) * dt
  dPi_w8 <- (C_w8 * p_w8 - C_w8 * c) * dt
  dPi8 <- (C_s8 * p_s8 + C_w8 * p_w8 - ((C_s8 + C_w8) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu8[i] <- N_w8 + dN_w8
  N_s_simu8[i] <- N_s8 + dN_s8
  #N_w_test_8[i] <- N_wt8 + dN_wt8
  #N_s_test_8[i] <- N_st8 + dN_st8
  E_simu8[i] <- E8 + dE8
  #E_test8[i] <- E_t8 + dE_test8
  C_s_simu8[i] <- C_s8 + dC_s8
  C_w_simu8[i] <- C_w8 + dC_w8
  cpue_s_simu8[i] <- cpue_s8 + dcpue_s8
  cpue_w_simu8[i] <- cpue_w8 + dcpue_w8
  Pi_sum_simu8[i] <- pi8 + dPi8
  Pi_s_simu8[i] <- pi_s8 + dPi_s8
  Pi_w_simu8[i] <- pi_w8 + dPi_w8  
  
  
}
```


```{r, echo = FALSE}
run_model <- function(r_s, k_s, q_s, p_s, r_w, k_w, q_w, p_w, c){
 
  # Derive effort
 E <- ((- c + k_s * p_s * q_s + k_w * p_w * q_w) * r_s * r_w)  /
   (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w) 
  
  # Derive weak stock biomass
 
  N_w <- (k_w * (c * q_w * r_s + k_s * p_s * q_s * (- q_w * r_s + q_s * r_w))) / 
    (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w)
  
 # Derive strong stock biomass
 
   N_s <- (k_s * (c * q_s * r_w + k_w * p_w * q_w * (q_w * r_s - q_s * r_w))) /
     (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w)
  
  # Build output
  output <- data.frame(E = E, N_s = N_s, N_w = N_w)
 
  # Return
  return(output)
 
 
}

sc_1 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 0.1, c = 0.05)
sc_2 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 0.2, c = 0.05)
sc_3 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 0.4, c = 0.05)
sc_4 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)
sc_5 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 0.75, p_w = 1, c = 0.05)
sc_6 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 0.5, p_w = 1, c = 0.05)
sc_7 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 0.2, p_w = 1, c = 0.05)
sc_8 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = .1, p_w = 1, c = 0.05)

sc_all <- bind_rows(sc_1, sc_2, sc_3, sc_4, sc_5, sc_6, sc_7, sc_8) %>% 
  rownames_to_column() %>% 
  rename(scenario = rowname) %>% 
  mutate(tset = 5) %>% 
  pivot_longer(cols = E:N_w,
               names_to = "variable",
               values_to = "value") %>% 
  mutate(price_ratio = case_when(
    scenario == "1" ~ "PR = 10",
    scenario == "2" ~ "PR = 5",
    scenario == "3" ~ "PR = 2.5",
    scenario == "4" ~ "PR = 1",
    scenario == "5" ~ "PR = 0.75",
    scenario == "6" ~ "PR = 0.5",
    scenario == "7" ~ "PR = 0.25",
    scenario == "8" ~ "PR = 0.1"
  )) %>% 
  pivot_wider(names_from = "variable",
              values_from = "value") %>% 
  mutate(b_values_s = N_s / 4,
         b_values_w = N_w / 2) %>% 
  pivot_longer(cols = N_s:N_w,
               names_to = "variable",
               values_to = "value") %>%
  pivot_longer(cols = b_values_s:b_values_w,
               names_to = "b_values",
               values_to = "b_v_k") %>% 
  pivot_longer(cols = E,
               names_to = "effort",
               values_to = "ef_value") %>% 
  mutate(variable = case_when(
    variable == "N_s" ~ "Ns*",
    variable == "N_w" ~ "Nw*"
  )) %>% 
  mutate(effort = case_when(
    effort == "E" ~ "E*"
  )) %>% 
  mutate(b_values = case_when(
    str_detect(b_values, "_w") ~ "Nw/Kw*",
    str_detect(b_values, "_s") ~ "Ns/Ks*"
  ))
```

```{r building df for the parameter space, echo = FALSE}
eq_par <- data.frame(parameter = c("q_w", "q_s", "k_w", "k_s", "r_w", "r_s", "p_w", "p_s", "c"),
                     "PR_10" =  c(0.1, 0.1, 4, 2, 0.8, 0.45, 1, 0.1, 0.05),
                     "PR_5" =   c(0.1, 0.1, 4, 2, 0.8, 0.45, 1, 0.2, 0.05),
                     "PR_2.5" = c(0.1, 0.1, 4, 2, 0.8, 0.45, 1, 0.4, 0.05),
                     "PR_1" =   c(0.1, 0.1, 4, 2, 0.8, 0.45, 1, 1, 0.05),
                     "PR_0.75" =c(0.1, 0.1, 4, 2, 0.8, 0.45, 0.75, 1, 0.05),
                     "PR_0.5" = c(0.1, 0.1, 4, 2, 0.8, 0.45, 0.5, 1, 0.05),
                     "PR_0.25" =c(0.1, 0.1, 4, 2, 0.8, 0.45, 0.25, 1, 0.05),
                     "PR_0.1" = c(0.1, 0.1, 4, 2, 0.8, 0.45, 0.1, 1, 0.05))

eq_par %>% 
  gt() %>%
  tab_header(title = "Parameter space for equilibrium points") %>% 
  cols_align(align = "center")
  
```


```{r, echo = FALSE}
effort_df <- cbind(E_simu1, E_simu2, E_simu3, E_simu4, E_simu5, E_simu6, E_simu7, E_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("E_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8")
         )

# effort_test_df <- cbind(E_test1, E_test2, E_test3, E_test4, E_test5, E_test6, E_test7, E_test8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("E_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")
#     )

nw_df <- cbind(N_w_simu1, N_w_simu2, N_w_simu3, N_w_simu4, N_w_simu5, N_w_simu6, N_w_simu7,N_w_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("N_w_simu"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8")) %>% 
  mutate(b_v_k = value/2)


ns_df <- cbind(N_s_simu1, N_s_simu2, N_s_simu3, N_s_simu4, N_s_simu5, N_s_simu6, N_s_simu7, N_s_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("N_s_simu"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8")) %>% 
  mutate(b_v_k = value/4)

# ns_t_df <- cbind(N_s_test_1, N_s_test_2, N_s_test_3, N_s_test_4, N_s_test_5, N_s_test_6, N_s_test_7, N_s_test_8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("N_s_test_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")) %>% 
#   mutate(b_v_k = value/4)
# 
# nw_t_df <- cbind(N_w_test_1, N_w_test_2, N_w_test_3, N_w_test_4, N_w_test_5, N_w_test_6, N_w_test_7, N_w_test_8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("N_w_test_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")) %>% 
#   mutate(b_v_k = value/2)

catch_s_df <- cbind(C_s_simu1, C_s_simu2, C_s_simu3, C_s_simu4, C_s_simu5, C_s_simu6, C_s_simu7, C_s_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("C_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

catch_w_df <- cbind(C_w_simu1, C_w_simu2, C_w_simu3, C_w_simu4, C_w_simu5, C_w_simu6, C_w_simu7, C_w_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("C_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))


cpue_s_df <- cbind(cpue_s_simu1, cpue_s_simu2, cpue_s_simu3, cpue_s_simu4, cpue_s_simu5, cpue_s_simu6, cpue_s_simu7, cpue_s_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("cpue_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))


cpue_w_df <- cbind(cpue_w_simu1, cpue_w_simu2, cpue_w_simu3, cpue_w_simu4, cpue_w_simu5, cpue_w_simu6, cpue_w_simu7, cpue_w_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("cpue_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

profits_df <- cbind(Pi_sum_simu1, Pi_sum_simu2, Pi_sum_simu3, Pi_sum_simu4, Pi_sum_simu5, Pi_sum_simu6, Pi_sum_simu7, Pi_sum_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_sum"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

profits_s_df <- cbind(Pi_s_simu1, Pi_s_simu2, Pi_s_simu3, Pi_s_simu4, Pi_s_simu5, Pi_s_simu6, Pi_s_simu7, Pi_s_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

profits_w_df <- cbind(Pi_w_simu1, Pi_w_simu2, Pi_w_simu3, Pi_w_simu4, Pi_w_simu5, Pi_w_simu6, Pi_w_simu7, Pi_w_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

# Gathered the results from each model scenario run into a single df

var_full <- bind_rows(effort_df, nw_df, ns_df, catch_s_df, catch_w_df, cpue_s_df, cpue_w_df, profits_df, profits_w_df, profits_s_df)

# Tidy dataset for plotting

var_plot <- var_full %>%
  mutate(price_ratio = case_when(
    str_detect(scenario_id, "1") ~ "PR = 10",
    str_detect(scenario_id, "2") ~ "PR = 5",
    str_detect(scenario_id, "3") ~ "PR = 2.5",
    str_detect(scenario_id, "4") ~ "PR = 1",
    str_detect(scenario_id, "5") ~ "PR = 0.75",
    str_detect(scenario_id, "6") ~ "PR = 0.5",
    str_detect(scenario_id, "7") ~ "PR = 0.25",
    str_detect(scenario_id, "8") ~ "PR = 0.1"
  )) %>% 
  mutate(variable_clean = case_when(
    str_detect(variable, "N_w_test") ~ "Weak stock test",
    str_detect(variable, "N_s_test") ~ "Strong stock test",    
    str_detect(variable, "N_w") ~ "Weak stock",
    str_detect(variable, "N_s") ~ "Strong stock",
    str_detect(variable, "E_simu") ~ "Effort simulation",
    str_detect(variable, "E_test") ~ "Effort test",
    str_detect(variable, "Pi_sum_") ~ "Profit sum",
    str_detect(variable, "Pi_s") ~ "Strong stock profits",
    str_detect(variable, "Pi_w") ~ "Weak stock profits",
    str_detect(variable, "cpue_w") ~ "Weak stock CPUE",
    str_detect(variable, "cpue_s") ~ "Strong stock CPUE",
    str_detect(variable, "C_w") ~ "Weak stock catch",
    str_detect(variable, "C_s") ~ "Strong stock catch"
  ))
```

```{r, echo = FALSE, fig.height=4, fig.width=8}
equal_scales_EWS <-
  var_plot %>% 
  filter(variable_clean %in% c("Effort simulation", "Weak stock", "Strong stock")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  geom_point(data = sc_all, 
             aes(x = tset, y = value, color = variable)) +
  geom_point(data = sc_all,
             aes(x = tset, y = ef_value, color = effort)) +
  facet_wrap(~ factor(price_ratio, 
                      levels = c("PR = 10",
                                 "PR = 5",
                                 "PR = 2.5",
                                 "PR = 1",
                                 "PR = 0.75",
                                 "PR = 0.5",
                                 "PR = 0.25",
                                 "PR = 0.1")),
             nrow = 1) +
  scale_color_manual(values = c("#1B9E77", "#1B9E77", "#D95F02", "#7570B3",  "#D95F02", "#7570B3")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "",
       y = "Nw, Ns, E",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

# equal_scales_EWS_test <-
#   var_plot %>% 
#   filter(variable_clean %in% c("Effort test", "Weak stock test", "Strong stock test")) %>% 
#   ggplot() +
#   geom_line(aes(x = tset/100, y = value, color = variable_clean),
#             size = .8,
#             alpha = .8,
#             show.legend = T) +
#   geom_point(data = sc_all, 
#              aes(x = tset, y = value, color = variable)) +
#   geom_point(data = sc_all, 
#              aes(x = tset, y = ef_value, color = effort)) +
#   facet_wrap(~ factor(price_ratio, 
#                       levels = c("PR = 10",
#                                  "PR = 5",
#                                  "PR = 2.5",
#                                  "PR = 1",
#                                  "PR = 0.75",
#                                  "PR = 0.5",
#                                  "PR = 0.25",
#                                  "PR = 0.1")),
#              nrow = 1) +
#   scale_color_manual(values = c("#1B9E77", "#1B9E77", "#D95F02", "#7570B3",  "#D95F02", "#7570B3")) +
# #  scale_y_continuous(breaks = seq(0, 50, 10)) +
#   labs(x = "",
#        y = "Nw, Ns, E",
#        color = "") +
#   theme_bw() +
#   theme(panel.grid.major.x = element_blank(),
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         strip.background = element_rect(fill = "transparent"),
#         strip.text = element_text(color = "black", size = 11),
#         axis.title.x = element_text(color = "black", size = 12),
#         axis.title.y = element_text(color = "black", size = 12, vjust = 2),
#         axis.text = element_text(color = "black", size = 10),
#         legend.position = "bottom")

dif_scales <-
  var_plot %>% 
  filter(variable_clean %in% c("Strong stock", "Weak stock")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = b_v_k, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = F) +
  geom_point(data = sc_all %>% filter(!variable == "E"), 
             aes(x = tset, y = b_v_k, color = b_values)) +
  facet_wrap(~ factor(price_ratio, 
                      levels = c("PR = 10",
                                 "PR = 5",
                                 "PR = 2.5",
                                 "PR = 1",
                                 "PR = 0.75",
                                 "PR = 0.5",
                                 "PR = 0.25",
                                 "PR = 0.1")),
             nrow = 1) +
  scale_color_manual(values = c("#D95F02", "#7570B3", "#D95F02", "#7570B3")) +
#  scale_x_continuous(breaks = seq(0, 500, 100)) +
  labs(x = "",
       y = "N/K (Nw, Ns)",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12, vjust = -2),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

equal_scales_CPE <-
  var_plot %>% 
  filter(variable_clean %in% c("Weak stock catch", "Strong stock catch", "Weak stock CPUE", "Strong stock CPUE")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  facet_wrap(~ factor(price_ratio, 
                      levels = c("PR = 10",
                                 "PR = 5",
                                 "PR = 2.5",
                                 "PR = 1",
                                 "PR = 0.75",
                                 "PR = 0.5",
                                 "PR = 0.25",
                                 "PR = 0.1")),
             nrow = 1) +
  scale_color_manual(values = c("#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "",
       y = "CPUE, Catch (S and W)",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

equal_scales_pi <-
  var_plot %>% 
  filter(variable_clean %in% c("Profit sum", "Weak stock profits", "Strong stock profits")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  facet_wrap(~ factor(price_ratio, 
                      levels = c("PR = 10",
                                 "PR = 5",
                                 "PR = 2.5",
                                 "PR = 1",
                                 "PR = 0.75",
                                 "PR = 0.5",
                                 "PR = 0.25",
                                 "PR = 0.1")),
             nrow = 1) +
  scale_color_manual(values = c("#FF7F00", "#CAB2D6", "#6A3D9A")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "Time (x100)",
       y = "Profits",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")
```

```{r, fig.height=15, fig.width=10, echo = FALSE}
equal_scales_EWS /
  dif_scales /
  equal_scales_CPE /
  equal_scales_pi +
  plot_annotation(tag_level = "A") 
```

Panel A shows the time series dynamics for the strong and weak stocks, and effort. Panel B shows the same data but without effort for better comparison. Panel C shows the CPUE and catch for the strong and weak stocks separately. Panel D shows the profits for the strong and weak stocks, and the total profits for the fishery through time.

**Negative equilibrium points for the weak stock only occur at high enough prices of the strong stock. If the price ratio ($PR = P_s/P_w$) is smaller than 0.25, both stock have positive equilibrium points (at a growth rate ratio ($r_s/r_w$) of ~2).**

- I think this figure (or a better version of it) should also go in the paper, because it clearly shows how effort increases a lot when we consider two species, and how it drives both of them to extremely low levels for most of the scenarios, but not all. 


### Scenarios for a range of productivity ratios:

```{r scenario 1 productivity ratio 2, echo = FALSE}
# set up the parameter space
q_s <- 0.1
q_w <- 0.1
k_s <- 4
k_w <- 2
r_s1 <- 1
r_w1 <- 0.5
p_s <- 1
p_w <- 1
alpha <- 1
c <- 0.05

# Initial values for the variables
N_w <- k_w

N_s <- k_s

E <- 0.1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu1 <- NaN*tset; N_w_simu1[1] <- N_w

N_s_simu1 <- NaN*tset; N_s_simu1[1] <- N_s

#N_w_test_1 <- NaN*tset; N_w_test_1[1] <- N_w

#N_s_test_1 <- NaN*tset; N_s_test_1[1] <- N_s

E_simu1 <- NaN*tset; E_simu1[1] <- E

#E_test1 <- NaN*tset; E_test1[1] <- E

C_s_simu1 <- NaN*tset; C_s_simu1[1] <- 1

C_w_simu1 <- NaN*tset; C_w_simu1[1] <- 1

cpue_s_simu1 <- NaN*tset; cpue_s_simu1[1] <- 1

cpue_w_simu1 <- NaN*tset; cpue_w_simu1[1] <- 1

Pi_sum_simu1 <- NaN*tset; Pi_sum_simu1[1] <- 2

Pi_s_simu1 <- NaN*tset; Pi_s_simu1[1] <- 1

Pi_w_simu1 <- NaN*tset; Pi_w_simu1[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w1 <- N_w_simu1[i-1]
  N_s1 <- N_s_simu1[i-1]
  #N_wt1 <- N_w_test_1[i-1]
  #N_st1 <- N_s_test_1[i-1]
  E1 <- E_simu1[i-1]
  #E_t1 <- E_test1[i-1]
  C_s1 <- C_s_simu1[i-1]
  C_w1 <- C_w_simu1[i-1]
  cpue_s1 <- cpue_s_simu1[i-1]
  cpue_w1 <- cpue_w_simu1[i-1]
  pi1 <- Pi_sum_simu1[i-1]
  pi_s1 <- Pi_s_simu1[i-1]
  pi_w1 <- Pi_w_simu1[i-1]
    
  # Calculate change in variable size at each time step
  dN_s1 <- (N_s1 * (r_s1 * (1 - (N_s1/k_s)) - q_s * E1)) * dt
  dN_w1 <- (N_w1 * (r_w1 * (1 - (N_w1/k_w)) - q_w * E1)) * dt
  #dN_st1 <- (N_st1 * (r_s * (1 - (N_st1/k_s)) - q_s * E_t1)) * dt
  #dN_wt1 <- (N_wt1 * (r_w * (1 - (N_wt1/k_w)) - q_w * E_t1)) * dt
  dE1 <- (alpha * E1 * (p_s * q_s * N_s1 + p_w * q_w * N_w1 - c)) * dt
  #dE_test1 <- ((p_s1 * q_s1 * N_st1 + p_w1 * q_w1 * N_wt1) - c) * dt
  dC_s1 <- (q_s * N_s1 * E1) * dt
  dC_w1 <- (q_w * N_w1 * E1) * dt
  dcpue_s1 <- (C_s1 / E1) * dt
  dcpue_w1 <- (C_w1 / E1) * dt
  dPi_s1 <- (C_s1 * p_s - C_s1 * c) * dt
  dPi_w1 <- (C_w1 * p_w - C_w1 * c) * dt
  dPi1 <- (C_s1 * p_s + C_w1 * p_w - ((C_s1 + C_w1) * c)) * dt
  # calculate total variable size and store in holding vectors
  
  N_w_simu1[i] <- N_w1 + dN_w1
  N_s_simu1[i] <- N_s1 + dN_s1
  #N_w_test_1[i] <- N_wt1 + dN_wt1
  #N_s_test_1[i] <- N_st1 + dN_st1
  E_simu1[i] <- E1 + dE1
  #E_test1[i] <- E_t1 + dE_test1
  C_s_simu1[i] <- C_s1 + dC_s1
  C_w_simu1[i] <- C_w1 + dC_w1
  cpue_s_simu1[i] <- cpue_s1 + dcpue_s1
  cpue_w_simu1[i] <- cpue_w1 + dcpue_w1
  Pi_sum_simu1[i] <- pi1 + dPi1
  Pi_s_simu1[i] <- pi_s1 + dPi_s1
  Pi_w_simu1[i] <- pi_w1 + dPi_w1
  
}
  

```


```{r scenario 2 productivity ratio 1.75, echo = FALSE}
r_s2 <- 1
r_w2 <- 0.57
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu2 <- NaN*tset; N_w_simu2[1] <- N_w

N_s_simu2 <- NaN*tset; N_s_simu2[1] <- N_s

#N_w_test_2 <- NaN*tset; N_w_test_2[1] <- N_w

#N_s_test_2 <- NaN*tset; N_s_test_2[1] <- N_s

E_simu2 <- NaN*tset; E_simu2[1] <- E

#E_test2 <- NaN*tset; E_test2[1] <- E

C_s_simu2 <- NaN*tset; C_s_simu2[1] <- 1

C_w_simu2 <- NaN*tset; C_w_simu2[1] <- 1

cpue_s_simu2 <- NaN*tset; cpue_s_simu2[1] <- 1

cpue_w_simu2 <- NaN*tset; cpue_w_simu2[1] <- 1

Pi_sum_simu2 <- NaN*tset; Pi_sum_simu2[1] <- 2

Pi_s_simu2 <- NaN*tset; Pi_s_simu2[1] <- 1

Pi_w_simu2 <- NaN*tset; Pi_w_simu2[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w2 <- N_w_simu2[i-1]
  N_s2 <- N_s_simu2[i-1]
  #N_wt2 <- N_w_test_2[i-1]
  #N_st2 <- N_s_test_2[i-1]
  E2 <- E_simu2[i-1]
  #E_t2 <- E_test2[i-1]
  C_s2 <- C_s_simu2[i-1]
  C_w2 <- C_w_simu2[i-1]
  cpue_s2 <- cpue_s_simu2[i-1]
  cpue_w2 <- cpue_w_simu2[i-1]
  pi2 <- Pi_sum_simu2[i-1]
  pi_s2 <- Pi_s_simu2[i-1]
  pi_w2 <- Pi_w_simu2[i-1]

  # Calculate change in variable size at each time step
  dN_s2 <- (N_s2 * (r_s2 * (1 - (N_s2/k_s)) - q_s * E2)) * dt
  dN_w2 <- (N_w2 * (r_w2 * (1 - (N_w2/k_w)) - q_w * E2)) * dt
  #dN_st2 <- (N_st2 * (r_s2 * (1 - (N_st2/k_s2)) - q_s2 * E_t2)) * dt
  #dN_wt2 <- (N_wt2 * (r_w2 * (1 - (N_wt2/k_w2)) - q_w2 * E_t2)) * dt
  dE2 <- (alpha * E2 * (p_s * q_s * N_s2 + p_w * q_w * N_w2 - c)) * dt
  #dE_test2 <- ((p_s2 * q_s2 * N_st2 + p_w2 * q_w2 * N_wt2) - c) * dt
  dC_s2 <- (q_s * N_s2 * E2) * dt
  dC_w2 <- (q_w * N_w2 * E2) * dt
  dcpue_s2 <- (C_s2 / E2) * dt
  dcpue_w2 <- (C_w2 / E2) * dt
  dPi_s2 <- (C_s2 * p_s - C_s2 * c) * dt
  dPi_w2 <- (C_w2 * p_w - C_w2 * c) * dt
  dPi2 <- (C_s2 * p_s + C_w2 * p_w - ((C_s2 + C_w2) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu2[i] <- N_w2 + dN_w2
  N_s_simu2[i] <- N_s2 + dN_s2
  #N_w_test_2[i] <- N_wt2 + dN_wt2
  #N_s_test_2[i] <- N_st2 + dN_st2
  E_simu2[i] <- E2 + dE2
  #E_test2[i] <- E_t2 + dE_test2
  C_s_simu2[i] <- C_s2 + dC_s2
  C_w_simu2[i] <- C_w2 + dC_w2
  cpue_s_simu2[i] <- cpue_s2 + dcpue_s2
  cpue_w_simu2[i] <- cpue_w2 + dcpue_w2
  Pi_sum_simu2[i] <- pi2 + dPi2
  Pi_s_simu2[i] <- pi_s2 + dPi_s2
  Pi_w_simu2[i] <- pi_w2 + dPi_w2
}
```



```{r scenario 3 productivity ratio 1.5, echo = FALSE}
# set up the parameter space
r_s3 <- 1
r_w3 <- 0.69
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu3 <- NaN*tset; N_w_simu3[1] <- N_w

N_s_simu3 <- NaN*tset; N_s_simu3[1] <- N_s

#N_w_test_3 <- NaN*tset; N_w_test_3[1] <- N_w

#N_s_test_3 <- NaN*tset; N_s_test_3[1] <- N_s

E_simu3 <- NaN*tset; E_simu3[1] <- E

#E_test3 <- NaN*tset; E_test3[1] <- E

C_s_simu3 <- NaN*tset; C_s_simu3[1] <- 1

C_w_simu3 <- NaN*tset; C_w_simu3[1] <- 1

cpue_s_simu3 <- NaN*tset; cpue_s_simu3[1] <- 1

cpue_w_simu3 <- NaN*tset; cpue_w_simu3[1] <- 1

Pi_sum_simu3 <- NaN*tset; Pi_sum_simu3[1] <- 2

Pi_s_simu3 <- NaN*tset; Pi_s_simu3[1] <- 1

Pi_w_simu3 <- NaN*tset; Pi_w_simu3[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w3 <- N_w_simu3[i-1]
  N_s3 <- N_s_simu3[i-1]
  #N_wt3 <- N_w_test_3[i-1]
  #N_st3 <- N_s_test_3[i-1]
  E3 <- E_simu3[i-1]
  #E_t3 <- E_test3[i-1]
  C_s3 <- C_s_simu3[i-1]
  C_w3 <- C_w_simu3[i-1]
  cpue_s3 <- cpue_s_simu3[i-1]
  cpue_w3 <- cpue_w_simu3[i-1]
  pi3 <- Pi_sum_simu3[i-1]
  pi_s3 <- Pi_s_simu3[i-1]
  pi_w3 <- Pi_w_simu3[i-1]

  # Calculate change in variable size at each time step
  dN_s3 <- (N_s3 * (r_s2 * (1 - (N_s3/k_s)) - q_s * E3)) * dt
  dN_w3 <- (N_w3 * (r_w2 * (1 - (N_w3/k_w)) - q_w * E3)) * dt
  #dN_st3 <- (N_st3 * (r_s3 * (1 - (N_st3/k_s3)) - q_s3 * E_t3)) * dt
  #dN_wt3 <- (N_wt3 * (r_w3 * (1 - (N_wt3/k_w3)) - q_w3 * E_t3)) * dt
  dE3 <- (alpha * E3 * (p_s * q_s * N_s3 + p_w * q_w * N_w3 - c)) * dt
  #dE_test3 <- ((p_s3 * q_s3 * N_st3 + p_w3 * q_w3 * N_wt3) - c) * dt
  dC_s3 <- (q_s * N_s3 * E3) * dt
  dC_w3 <- (q_w * N_w3 * E3) * dt
  dcpue_s3 <- (C_s3 / E3) * dt
  dcpue_w3 <- (C_w3 / E3) * dt
  dPi_s3 <- (C_s3 * p_s - C_s3 * c) * dt
  dPi_w3 <- (C_w3 * p_w - C_w3 * c) * dt
  dPi3 <- (C_s3 * p_s + C_w3 * p_w - ((C_s3 + C_w3) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu3[i] <- N_w3 + dN_w3
  N_s_simu3[i] <- N_s3 + dN_s3
  #N_w_test_3[i] <- N_wt3 + dN_wt3
  #N_s_test_3[i] <- N_st3 + dN_st3
  E_simu3[i] <- E3 + dE3
  #E_test3[i] <- E_t3 + dE_test3
  C_s_simu3[i] <- C_s3 + dC_s3
  C_w_simu3[i] <- C_w3 + dC_w3
  cpue_s_simu3[i] <- cpue_s3 + dcpue_s3
  cpue_w_simu3[i] <- cpue_w3 + dcpue_w3
  Pi_sum_simu3[i] <- pi3 + dPi3
  Pi_s_simu3[i] <- pi_s3 + dPi_s3
  Pi_w_simu3[i] <- pi_w3 + dPi_w3

}
```


```{r scenario 4 productivity ratio 1.25, echo = FALSE}
# set up the parameter space
r_s4 <- 1
r_w4 <- 0.8
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu4 <- NaN*tset; N_w_simu4[1] <- N_w

N_s_simu4 <- NaN*tset; N_s_simu4[1] <- N_s

#N_w_test_4 <- NaN*tset; N_w_test_4[1] <- N_w

#N_s_test_4 <- NaN*tset; N_s_test_4[1] <- N_s

E_simu4 <- NaN*tset; E_simu4[1] <- E

#E_test4 <- NaN*tset; E_test4[1] <- E

C_s_simu4 <- NaN*tset; C_s_simu4[1] <- 1

C_w_simu4 <- NaN*tset; C_w_simu4[1] <- 1

cpue_s_simu4 <- NaN*tset; cpue_s_simu4[1] <- 1

cpue_w_simu4 <- NaN*tset; cpue_w_simu4[1] <- 1

Pi_sum_simu4 <- NaN*tset; Pi_sum_simu4[1] <- 2

Pi_s_simu4 <- NaN*tset; Pi_s_simu4[1] <- 1

Pi_w_simu4 <- NaN*tset; Pi_w_simu4[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w4 <- N_w_simu4[i-1]
  N_s4 <- N_s_simu4[i-1]
  #N_wt4 <- N_w_test_4[i-1]
  #N_st4 <- N_s_test_4[i-1]
  E4 <- E_simu4[i-1]
  #E_t4 <- E_test4[i-1]
  C_s4 <- C_s_simu4[i-1]
  C_w4 <- C_w_simu4[i-1]
  cpue_s4 <- cpue_s_simu4[i-1]
  cpue_w4 <- cpue_w_simu4[i-1]
  pi4 <- Pi_sum_simu4[i-1]
  pi_s4 <- Pi_s_simu4[i-1]
  pi_w4 <- Pi_w_simu4[i-1]

  # Calculate change in variable size at each time step
  dN_s4 <- (N_s4 * (r_s4 * (1 - (N_s4/k_s)) - q_s * E4)) * dt
  dN_w4 <- (N_w4 * (r_w4 * (1 - (N_w4/k_w)) - q_w * E4)) * dt
  #dN_st4 <- (N_st4 * (r_s4 * (1 - (N_st4/k_s4)) - q_s4 * E_t4)) * dt
  #dN_wt4 <- (N_wt4 * (r_w4 * (1 - (N_wt4/k_w4)) - q_w4 * E_t4)) * dt
  dE4 <- (alpha * E4 * (p_s * q_s * N_s4 + p_w * q_w * N_w4 - c)) * dt
  #dE_test4 <- ((p_s4 * q_s4 * N_st4 + p_w4 * q_w4 * N_wt4) - c) * dt
  dC_s4 <- (q_s * N_s4 * E4) * dt
  dC_w4 <- (q_w * N_w4 * E4) * dt
  dcpue_s4 <- (C_s4 / E4) * dt
  dcpue_w4 <- (C_w4 / E4) * dt
  dPi_s4 <- (C_s4 * p_s - C_s4 * c) * dt
  dPi_w4 <- (C_w4 * p_w - C_w4 * c) * dt
  dPi4 <- (C_s4 * p_s + C_w4 * p_w - ((C_s4 + C_w4) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu4[i] <- N_w4 + dN_w4
  N_s_simu4[i] <- N_s4 + dN_s4
  #N_w_test_4[i] <- N_wt4 + dN_wt4
  #N_s_test_4[i] <- N_st4 + dN_st4
  E_simu4[i] <- E4 + dE4
  #E_test4[i] <- E_t4 + dE_test4
  C_s_simu4[i] <- C_s4 + dC_s4
  C_w_simu4[i] <- C_w4 + dC_w4
  cpue_s_simu4[i] <- cpue_s4 + dcpue_s4
  cpue_w_simu4[i] <- cpue_w4 + dcpue_w4
  Pi_sum_simu4[i] <- pi4 + dPi4
  Pi_s_simu4[i] <- pi_s4 + dPi_s4
  Pi_w_simu4[i] <- pi_w4 + dPi_w4
  
}
```



```{r scenario 5 productivity ratio 1.1, echo = FALSE}
# set up the parameter space
r_s5 <- 1
r_w5 <- 0.9
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu5 <- NaN*tset; N_w_simu5[1] <- N_w

N_s_simu5 <- NaN*tset; N_s_simu5[1] <- N_s

#N_w_test_5 <- NaN*tset; N_w_test_5[1] <- N_w

#N_s_test_5 <- NaN*tset; N_s_test_5[1] <- N_s

E_simu5 <- NaN*tset; E_simu5[1] <- E

#E_test5 <- NaN*tset; E_test5[1] <- E

C_s_simu5 <- NaN*tset; C_s_simu5[1] <- 1

C_w_simu5 <- NaN*tset; C_w_simu5[1] <- 1

cpue_s_simu5 <- NaN*tset; cpue_s_simu5[1] <- 1

cpue_w_simu5 <- NaN*tset; cpue_w_simu5[1] <- 1

Pi_sum_simu5 <- NaN*tset; Pi_sum_simu5[1] <- 2

Pi_s_simu5 <- NaN*tset; Pi_s_simu5[1] <- 1

Pi_w_simu5 <- NaN*tset; Pi_w_simu5[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w5 <- N_w_simu5[i-1]
  N_s5 <- N_s_simu5[i-1]
  #N_wt5 <- N_w_test_5[i-1]
  #N_st5 <- N_s_test_5[i-1]
  E5 <- E_simu5[i-1]
  #E_t5 <- E_test5[i-1]
  C_s5 <- C_s_simu5[i-1]
  C_w5 <- C_w_simu5[i-1]
  cpue_s5 <- cpue_s_simu5[i-1]
  cpue_w5 <- cpue_w_simu5[i-1]
  pi5 <- Pi_sum_simu5[i-1]
  pi_s5 <- Pi_s_simu5[i-1]
  pi_w5 <- Pi_w_simu5[i-1]

  # Calculate change in variable size at each time step
  dN_s5 <- (N_s5 * (r_s5 * (1 - (N_s5/k_s)) - q_s * E5)) * dt
  dN_w5 <- (N_w5 * (r_w5 * (1 - (N_w5/k_w)) - q_w * E5)) * dt
  #dN_st5 <- (N_st5 * (r_s5 * (1 - (N_st5/k_s5)) - q_s5 * E_t5)) * dt
  #dN_wt5 <- (N_wt5 * (r_w5 * (1 - (N_wt5/k_w5)) - q_w5 * E_t5)) * dt
  dE5 <- (alpha * E5 * (p_s * q_s * N_s5 + p_w * q_w * N_w5 - c)) * dt
  #dE_test5 <- ((p_s5 * q_s5 * N_st5 + p_w5 * q_w5 * N_wt5) - c) * dt
  dC_s5 <- (q_s * N_s5 * E5) * dt
  dC_w5 <- (q_w * N_w5 * E5) * dt
  dcpue_s5 <- (C_s5 / E5) * dt
  dcpue_w5 <- (C_w5 / E5) * dt
  dPi_s5 <- (C_s5 * p_s - C_s5 * c) * dt
  dPi_w5 <- (C_w5 * p_w - C_w5 * c) * dt
  dPi5 <- (C_s5 * p_s + C_w5 * p_w - ((C_s5 + C_w5) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu5[i] <- N_w5 + dN_w5
  N_s_simu5[i] <- N_s5 + dN_s5
  #N_w_test_5[i] <- N_wt5 + dN_wt5
  #N_s_test_5[i] <- N_st5 + dN_st5
  E_simu5[i] <- E5 + dE5
  #E_test5[i] <- E_t5 + dE_test5
  C_s_simu5[i] <- C_s5 + dC_s5
  C_w_simu5[i] <- C_w5 + dC_w5
  cpue_s_simu5[i] <- cpue_s5 + dcpue_s5
  cpue_w_simu5[i] <- cpue_w5 + dcpue_w5
  Pi_sum_simu5[i] <- pi5 + dPi5
  Pi_s_simu5[i] <- pi_s5 + dPi_s5
  Pi_w_simu5[i] <- pi_w5 + dPi_w5  
}
```




```{r scenario 6 productivity ratio 1, echo = FALSE}
r_s6 <- 1
r_w6 <- 1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu6 <- NaN*tset; N_w_simu6[1] <- N_w

N_s_simu6 <- NaN*tset; N_s_simu6[1] <- N_s

#N_w_test_6 <- NaN*tset; N_w_test_6[1] <- N_w

#N_s_test_6 <- NaN*tset; N_s_test_6[1] <- N_s

E_simu6 <- NaN*tset; E_simu6[1] <- E

#E_test6 <- NaN*tset; E_test6[1] <- E

C_s_simu6 <- NaN*tset; C_s_simu6[1] <- 1

C_w_simu6 <- NaN*tset; C_w_simu6[1] <- 1

cpue_s_simu6 <- NaN*tset; cpue_s_simu6[1] <- 1

cpue_w_simu6 <- NaN*tset; cpue_w_simu6[1] <- 1

Pi_sum_simu6 <- NaN*tset; Pi_sum_simu6[1] <- 2

Pi_s_simu6 <- NaN*tset; Pi_s_simu6[1] <- 1

Pi_w_simu6 <- NaN*tset; Pi_w_simu6[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w6 <- N_w_simu6[i-1]
  N_s6 <- N_s_simu6[i-1]
  #N_wt6 <- N_w_test_6[i-1]
  #N_st6 <- N_s_test_6[i-1]
  E6 <- E_simu6[i-1]
  #E_t6 <- E_test6[i-1]
  C_s6 <- C_s_simu6[i-1]
  C_w6 <- C_w_simu6[i-1]
  cpue_s6 <- cpue_s_simu6[i-1]
  cpue_w6 <- cpue_w_simu6[i-1]
  pi6 <- Pi_sum_simu6[i-1]
  pi_s6 <- Pi_s_simu6[i-1]
  pi_w6 <- Pi_w_simu6[i-1]

  # Calculate change in variable size at each time step
  dN_s6 <- (N_s6 * (r_s6 * (1 - (N_s6/k_s)) - q_s * E6)) * dt
  dN_w6 <- (N_w6 * (r_w6 * (1 - (N_w6/k_w)) - q_w * E6)) * dt
  #dN_st6 <- (N_st6 * (r_s6 * (1 - (N_st6/k_s6)) - q_s6 * E_t6)) * dt
  #dN_wt6 <- (N_wt6 * (r_w6 * (1 - (N_wt6/k_w6)) - q_w6 * E_t6)) * dt
  dE6 <- (alpha * E6 * (p_s * q_s * N_s6 + p_w * q_w * N_w6 - c)) * dt
  #dE_test6 <- ((p_s6 * q_s6 * N_st6 + p_w6 * q_w6 * N_wt6) - c) * dt
  dC_s6 <- (q_s * N_s6 * E6) * dt
  dC_w6 <- (q_w * N_w6 * E6) * dt
  dcpue_s6 <- (C_s6 / E6) * dt
  dcpue_w6 <- (C_w6 / E6) * dt
  dPi_s6 <- (C_s6 * p_s - C_s6 * c) * dt
  dPi_w6 <- (C_w6 * p_w - C_w6 * c) * dt
  dPi6 <- (C_s6 * p_s + C_w6 * p_w - ((C_s6 + C_w6) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  N_w_simu6[i] <- N_w6 + dN_w6
  N_s_simu6[i] <- N_s6 + dN_s6
  #N_w_test_6[i] <- N_wt6 + dN_wt6
  #N_s_test_6[i] <- N_st6 + dN_st6
  E_simu6[i] <- E6 + dE6
  #E_test6[i] <- E_t6 + dE_test6
  C_s_simu6[i] <- C_s6 + dC_s6
  C_w_simu6[i] <- C_w6 + dC_w6
  cpue_s_simu6[i] <- cpue_s6 + dcpue_s6
  cpue_w_simu6[i] <- cpue_w6 + dcpue_w6
  Pi_sum_simu6[i] <- pi6 + dPi6
  Pi_s_simu6[i] <- pi_s6 + dPi_s6
  Pi_w_simu6[i] <- pi_w6 + dPi_w6  
  
}
```

```{r, echo = FALSE}
run_model <- function(r_s, k_s, q_s, p_s, r_w, k_w, q_w, p_w, c){
 
  # Derive effort
 E <- ((- c + k_s * p_s * q_s + k_w * p_w * q_w) * r_s * r_w)  /
   (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w) 
  
  # Derive weak stock biomass
 
  N_w <- (k_w * (c * q_w * r_s + k_s * p_s * q_s * (- q_w * r_s + q_s * r_w))) / 
    (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w)
  
 # Derive strong stock biomass
 
   N_s <- (k_s * (c * q_s * r_w + k_w * p_w * q_w * (q_w * r_s - q_s * r_w))) /
     (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w)
  
  # Build output
  output <- data.frame(E = E, N_s = N_s, N_w = N_w)
 
  # Return
  return(output)
 
 
}

sc_r_1 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 1, r_w = 0.5, p_s = 1, p_w = 1, c = 0.05)
sc_r_2 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 1, r_w = 0.57, p_s = 1, p_w = 1, c = 0.05)
sc_r_3 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 1, r_w = 0.69, p_s = 1, p_w = 1, c = 0.05)
sc_r_4 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 1, r_w = 0.8, p_s = 1, p_w = 1, c = 0.05)
sc_r_5 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 1, r_w = 0.9, p_s = 1, p_w = 1, c = 0.05)
sc_r_6 <- run_model(q_s = 0.1, q_w = 0.1, k_s = 4, k_w = 2, r_s = 1, r_w = 1, p_s = 1, p_w = 1, c = 0.05)

sc_r_all <- bind_rows(sc_r_1, sc_r_2, sc_r_3, sc_r_4, sc_r_5, sc_r_6) %>% 
  rownames_to_column() %>% 
  rename(scenario = rowname) %>% 
  mutate(tset = 5) %>% 
  pivot_longer(cols = E:N_w,
               names_to = "variable",
               values_to = "value") %>% 
  mutate(price_ratio = case_when(
    scenario == "1" ~ "RR = 2",
    scenario == "2" ~ "RR = 1.75",
    scenario == "3" ~ "RR = 1.5",
    scenario == "4" ~ "RR = 1.25",
    scenario == "5" ~ "RR = 1.1",
    scenario == "6" ~ "RR = 1"
  )) %>% 
  pivot_wider(names_from = "variable",
              values_from = "value") %>% 
  mutate(b_values_s = N_s / k_s,
         b_values_w = N_w / k_w) %>% 
  pivot_longer(cols = N_s:N_w,
               names_to = "variable",
               values_to = "value") %>%
  pivot_longer(cols = b_values_s:b_values_w,
               names_to = "b_values",
               values_to = "b_v_k") %>% 
  pivot_longer(cols = E,
               names_to = "effort",
               values_to = "ef_value") %>% 
  mutate(variable = case_when(
    variable == "N_s" ~ "Ns*",
    variable == "N_w" ~ "Nw*"
  )) %>% 
  mutate(effort = case_when(
    effort == "E" ~ "E*"
  )) %>% 
  mutate(b_values = case_when(
    str_detect(b_values, "_w") ~ "Nw/Kw*",
    str_detect(b_values, "_s") ~ "Ns/Ks*"
  ))
```

```{r building df for the growth rate parameter space, echo = FALSE}
eq_par <- data.frame(parameter = c("q_w", "q_s", "k_w", "k_s", "r_w", "r_s", "p_w", "p_s", "c"),
                     "RR_2" =    c(0.1, 0.1, 4, 2, 1, 0.5, 1, 1, 0.05),
                     "RR_1.75" = c(0.1, 0.1, 4, 2, 1, 0.57, 1, 1, 0.05),
                     "RR_1.5" =  c(0.1, 0.1, 4, 2, 1, 0.69, 1, 1, 0.05),
                     "RR_1.25" = c(0.1, 0.1, 4, 2, 1, 0.8, 1, 1, 0.05),
                     "RR_1.1" =  c(0.1, 0.1, 4, 2, 1, 0.9, 1, 1, 0.05),
                     "RR_1" =    c(0.1, 0.1, 4, 2, 1, 1, 1, 1, 0.05))

eq_par %>% 
  gt() %>%
  tab_header(title = "Parameter space for equilibrium points") %>% 
  cols_align(align = "center")
  
```


```{r, echo = FALSE}
effort_df <- cbind(E_simu1, E_simu2, E_simu3, E_simu4, E_simu5, E_simu6, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("E_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6")
         )

# effort_test_df <- cbind(E_test1, E_test2, E_test3, E_test4, E_test5, E_test6, E_test7, E_test8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("E_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")
#     )

nw_df <- cbind(N_w_simu1, N_w_simu2, N_w_simu3, N_w_simu4, N_w_simu5, N_w_simu6, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("N_w_simu"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6")) %>% 
  mutate(b_v_k = value/k_w)


ns_df <- cbind(N_s_simu1, N_s_simu2, N_s_simu3, N_s_simu4, N_s_simu5, N_s_simu6, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("N_s_simu"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6")) %>% 
  mutate(b_v_k = value/k_s)

# ns_t_df <- cbind(N_s_test_1, N_s_test_2, N_s_test_3, N_s_test_4, N_s_test_5, N_s_test_6, N_s_test_7, N_s_test_8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("N_s_test_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")) %>% 
#   mutate(b_v_k = value/4)
# 
# nw_t_df <- cbind(N_w_test_1, N_w_test_2, N_w_test_3, N_w_test_4, N_w_test_5, N_w_test_6, N_w_test_7, N_w_test_8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("N_w_test_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")) %>% 
#   mutate(b_v_k = value/2)

catch_s_df <- cbind(C_s_simu1, C_s_simu2, C_s_simu3, C_s_simu4, C_s_simu5, C_s_simu6, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("C_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6"))

catch_w_df <- cbind(C_w_simu1, C_w_simu2, C_w_simu3, C_w_simu4, C_w_simu5, C_w_simu6, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("C_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6"))


cpue_s_df <- cbind(cpue_s_simu1, cpue_s_simu2, cpue_s_simu3, cpue_s_simu4, cpue_s_simu5, cpue_s_simu6, 
                   tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("cpue_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6"))


cpue_w_df <- cbind(cpue_w_simu1, cpue_w_simu2, cpue_w_simu3, cpue_w_simu4, cpue_w_simu5, cpue_w_simu6, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("cpue_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6"))

profits_df <- cbind(Pi_sum_simu1, Pi_sum_simu2, Pi_sum_simu3, Pi_sum_simu4, Pi_sum_simu5, Pi_sum_simu6,tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_sum"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6"))

profits_s_df <- cbind(Pi_s_simu1, Pi_s_simu2, Pi_s_simu3, Pi_s_simu4, Pi_s_simu5, Pi_s_simu6,tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6"))

profits_w_df <- cbind(Pi_w_simu1, Pi_w_simu2, Pi_w_simu3, Pi_w_simu4, Pi_w_simu5, Pi_w_simu6, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6"))

# Gathered the results from each model scenario run into a single df

var_full_r <- bind_rows(effort_df, nw_df, ns_df, catch_s_df, catch_w_df, cpue_s_df, cpue_w_df, profits_df, profits_w_df, profits_s_df)

# Tidy dataset for plotting

var_plot_r <- var_full_r %>%
  mutate(price_ratio = case_when(
    str_detect(scenario_id, "1") ~ "RR = 2",
    str_detect(scenario_id, "2") ~ "RR = 1.75",
    str_detect(scenario_id, "3") ~ "RR = 1.5",
    str_detect(scenario_id, "4") ~ "RR = 1.25",
    str_detect(scenario_id, "5") ~ "RR = 1.1",
    str_detect(scenario_id, "6") ~ "RR = 1"
  )) %>% 
  mutate(variable_clean = case_when(
    str_detect(variable, "N_w") ~ "Weak stock",
    str_detect(variable, "N_s") ~ "Strong stock",
    str_detect(variable, "E_simu") ~ "Effort simulation",
    str_detect(variable, "Pi_sum_") ~ "Profit sum",
    str_detect(variable, "Pi_s") ~ "Strong stock profits",
    str_detect(variable, "Pi_w") ~ "Weak stock profits",
    str_detect(variable, "cpue_w") ~ "Weak stock CPUE",
    str_detect(variable, "cpue_s") ~ "Strong stock CPUE",
    str_detect(variable, "C_w") ~ "Weak stock catch",
    str_detect(variable, "C_s") ~ "Strong stock catch"
  ))
```

```{r, echo = FALSE, fig.height=4, fig.width=8}
equal_scales_EWS_r <-
  var_plot_r %>% 
  filter(variable_clean %in% c("Effort simulation", "Weak stock", "Strong stock")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  geom_point(data = sc_r_all, 
             aes(x = tset, y = value, color = variable)) +
  geom_point(data = sc_r_all,
             aes(x = tset, y = ef_value, color = effort)) +
  facet_wrap(~ factor(price_ratio, 
                      levels = c("RR = 2",
                                 "RR = 1.75",
                                 "RR = 1.5",
                                 "RR = 1.25",
                                 "RR = 1.1",
                                 "RR = 1")),
             nrow = 1) +
  scale_color_manual(values = c("#1B9E77", "#1B9E77", "#D95F02", "#7570B3",  "#D95F02", "#7570B3")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "",
       y = "Nw, Ns, E",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

# equal_scales_EWS_test <-
#   var_plot %>% 
#   filter(variable_clean %in% c("Effort test", "Weak stock test", "Strong stock test")) %>% 
#   ggplot() +
#   geom_line(aes(x = tset/100, y = value, color = variable_clean),
#             size = .8,
#             alpha = .8,
#             show.legend = T) +
#   geom_point(data = sc_all, 
#              aes(x = tset, y = value, color = variable)) +
#   geom_point(data = sc_all, 
#              aes(x = tset, y = ef_value, color = effort)) +
#   facet_wrap(~ factor(price_ratio, 
#                       levels = c("PR = 10",
#                                  "PR = 5",
#                                  "PR = 2.5",
#                                  "PR = 1",
#                                  "PR = 0.75",
#                                  "PR = 0.5",
#                                  "PR = 0.25",
#                                  "PR = 0.1")),
#              nrow = 1) +
#   scale_color_manual(values = c("#1B9E77", "#1B9E77", "#D95F02", "#7570B3",  "#D95F02", "#7570B3")) +
# #  scale_y_continuous(breaks = seq(0, 50, 10)) +
#   labs(x = "",
#        y = "Nw, Ns, E",
#        color = "") +
#   theme_bw() +
#   theme(panel.grid.major.x = element_blank(),
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         strip.background = element_rect(fill = "transparent"),
#         strip.text = element_text(color = "black", size = 11),
#         axis.title.x = element_text(color = "black", size = 12),
#         axis.title.y = element_text(color = "black", size = 12, vjust = 2),
#         axis.text = element_text(color = "black", size = 10),
#         legend.position = "bottom")

dif_scales_r <-
  var_plot_r %>% 
  filter(variable_clean %in% c("Strong stock", "Weak stock")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = b_v_k, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = F) +
  geom_point(data = sc_r_all %>% filter(!variable == "E"), 
             aes(x = tset, y = b_v_k, color = b_values)) +
  facet_wrap(~ factor(price_ratio, 
                      levels = c("RR = 2",
                                 "RR = 1.75",
                                 "RR = 1.5",
                                 "RR = 1.25",
                                 "RR = 1.1",
                                 "RR = 1")),
             nrow = 1) +
  scale_color_manual(values = c("#D95F02", "#7570B3", "#D95F02", "#7570B3")) +
#  scale_x_continuous(breaks = seq(0, 500, 100)) +
  labs(x = "",
       y = "N/K (Nw, Ns)",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12, vjust = -2),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

equal_scales_CPE_r <-
  var_plot_r %>% 
  filter(variable_clean %in% c("Weak stock catch", "Strong stock catch", "Weak stock CPUE", "Strong stock CPUE")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  facet_wrap(~ factor(price_ratio, 
                      levels = c("RR = 2",
                                 "RR = 1.75",
                                 "RR = 1.5",
                                 "RR = 1.25",
                                 "RR = 1.1",
                                 "RR = 1")),
             nrow = 1) +
  scale_color_manual(values = c("#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "",
       y = "CPUE, Catch (S and W)",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

equal_scales_pi_r <-
  var_plot_r %>% 
  filter(variable_clean %in% c("Profit sum", "Weak stock profits", "Strong stock profits")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  facet_wrap(~ factor(price_ratio, 
                      levels = c("RR = 2",
                                 "RR = 1.75",
                                 "RR = 1.5",
                                 "RR = 1.25",
                                 "RR = 1.1",
                                 "RR = 1")),
             nrow = 1) +
  scale_color_manual(values = c("#FF7F00", "#CAB2D6", "#6A3D9A")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "Time (x100)",
       y = "Profits",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")
```

```{r, fig.height=15, fig.width=10, echo = FALSE}
equal_scales_EWS_r /
  dif_scales_r /
  equal_scales_CPE_r /
  equal_scales_pi_r +
  plot_annotation(tag_level = "A") 
```

### Scenarios for a range of catchability values

```{r scenario 1 catchability ratio 10, echo = FALSE}
# set up the parameter space
q_s1 <- 0.9
q_w1 <- 0.09
k_s <- 4
k_w <- 2
r_s <- 0.8
r_w <- 0.45
p_s <- 1
p_w <- 1
alpha <- 1
c <- 0.05

# Initial values for the variables
N_w <- k_w

N_s <- k_s

E <- 0.1
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu1 <- NaN*tset; N_w_simu1[1] <- N_w

N_s_simu1 <- NaN*tset; N_s_simu1[1] <- N_s

#N_w_test_1 <- NaN*tset; N_w_test_1[1] <- N_w

#N_s_test_1 <- NaN*tset; N_s_test_1[1] <- N_s

E_simu1 <- NaN*tset; E_simu1[1] <- E

#E_test1 <- NaN*tset; E_test1[1] <- E

C_s_simu1 <- NaN*tset; C_s_simu1[1] <- 1

C_w_simu1 <- NaN*tset; C_w_simu1[1] <- 1

cpue_s_simu1 <- NaN*tset; cpue_s_simu1[1] <- 1

cpue_w_simu1 <- NaN*tset; cpue_w_simu1[1] <- 1

Pi_sum_simu1 <- NaN*tset; Pi_sum_simu1[1] <- 2

Pi_s_simu1 <- NaN*tset; Pi_s_simu1[1] <- 1

Pi_w_simu1 <- NaN*tset; Pi_w_simu1[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w1 <- N_w_simu1[i-1]
  N_s1 <- N_s_simu1[i-1]
  #N_wt1 <- N_w_test_1[i-1]
  #N_st1 <- N_s_test_1[i-1]
  E1 <- E_simu1[i-1]
  #E_t1 <- E_test1[i-1]
  C_s1 <- C_s_simu1[i-1]
  C_w1 <- C_w_simu1[i-1]
  cpue_s1 <- cpue_s_simu1[i-1]
  cpue_w1 <- cpue_w_simu1[i-1]
  pi1 <- Pi_sum_simu1[i-1]
  pi_s1 <- Pi_s_simu1[i-1]
  pi_w1 <- Pi_w_simu1[i-1]

  # Calculate change in variable size at each time step
  dN_s1 <- (N_s1 * (r_s * (1 - (N_s1/k_s)) - q_s1 * E1)) * dt
  dN_w1 <- (N_w1 * (r_w * (1 - (N_w1/k_w)) - q_w1 * E1)) * dt
  #dN_st1 <- (N_st1 * (r_s1 * (1 - (N_st1/k_s1)) - q_s1 * E_t1)) * dt
  #dN_wt1 <- (N_wt1 * (r_w1 * (1 - (N_wt1/k_w1)) - q_w1 * E_t1)) * dt
  dE1 <- (alpha * E1 * (p_s * q_s1 * N_s1 + p_w * q_w1 * N_w1 - c)) * dt
  #dE_test1 <- ((p_s1 * q_s1 * N_st1 + p_w1 * q_w1 * N_wt1) - c) * dt
  dC_s1 <- (q_s1 * N_s1 * E1) * dt
  dC_w1 <- (q_w1 * N_w1 * E1) * dt
  dcpue_s1 <- (C_s1 / E1) * dt
  dcpue_w1 <- (C_w1 / E1) * dt
  dPi_s1 <- (C_s1 * p_s - C_s1 * c) * dt
  dPi_w1 <- (C_w1 * p_w - C_w1 * c) * dt
  dPi1 <- (C_s1 * p_s + C_w1 * p_w - ((C_s1 + C_w1) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu1[i] <- N_w1 + dN_w1
  N_s_simu1[i] <- N_s1 + dN_s1
  #N_w_test_1[i] <- N_wt1 + dN_wt1
  #N_s_test_1[i] <- N_st1 + dN_st1
  E_simu1[i] <- E1 + dE1
  #E_test1[i] <- E_t1 + dE_test1
  C_s_simu1[i] <- C_s1 + dC_s1
  C_w_simu1[i] <- C_w1 + dC_w1
  cpue_s_simu1[i] <- cpue_s1 + dcpue_s1
  cpue_w_simu1[i] <- cpue_w1 + dcpue_w1
  Pi_sum_simu1[i] <- pi1 + dPi1
  Pi_s_simu1[i] <- pi_s1 + dPi_s1
  Pi_w_simu1[i] <- pi_w1 + dPi_w1  
  
}
```


```{r scenario 2 catchability ratio 5, echo = FALSE}
# set up the parameter space
q_s2 <- 0.9
q_w2 <- 0.18
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu2 <- NaN*tset; N_w_simu2[1] <- N_w

N_s_simu2 <- NaN*tset; N_s_simu2[1] <- N_s

#N_w_test_2 <- NaN*tset; N_w_test_2[1] <- N_w

#N_s_test_2 <- NaN*tset; N_s_test_2[1] <- N_s

E_simu2 <- NaN*tset; E_simu2[1] <- E

#E_test2 <- NaN*tset; E_test2[1] <- E

C_s_simu2 <- NaN*tset; C_s_simu2[1] <- 1

C_w_simu2 <- NaN*tset; C_w_simu2[1] <- 1

cpue_s_simu2 <- NaN*tset; cpue_s_simu2[1] <- 1

cpue_w_simu2 <- NaN*tset; cpue_w_simu2[1] <- 1

Pi_sum_simu2 <- NaN*tset; Pi_sum_simu2[1] <- 2

Pi_s_simu2 <- NaN*tset; Pi_s_simu2[1] <- 1

Pi_w_simu2 <- NaN*tset; Pi_w_simu2[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w2 <- N_w_simu2[i-1]
  N_s2 <- N_s_simu2[i-1]
  #N_wt2 <- N_w_test_2[i-1]
  #N_st2 <- N_s_test_2[i-1]
  E2 <- E_simu2[i-1]
  #E_t2 <- E_test2[i-1]
  C_s2 <- C_s_simu2[i-1]
  C_w2 <- C_w_simu2[i-1]
  cpue_s2 <- cpue_s_simu2[i-1]
  cpue_w2 <- cpue_w_simu2[i-1]
  pi2 <- Pi_sum_simu2[i-1]
  pi_s2 <- Pi_s_simu2[i-1]
  pi_w2 <- Pi_w_simu2[i-1]

  # Calculate change in variable size at each time step
  dN_s2 <- (N_s2 * (r_s * (1 - (N_s2/k_s)) - q_s2 * E2)) * dt
  dN_w2 <- (N_w2 * (r_w * (1 - (N_w2/k_w)) - q_w2 * E2)) * dt
  #dN_st2 <- (N_st2 * (r_s2 * (1 - (N_st2/k_s2)) - q_s2 * E_t2)) * dt
  #dN_wt2 <- (N_wt2 * (r_w2 * (1 - (N_wt2/k_w2)) - q_w2 * E_t2)) * dt
  dE2 <- (alpha * E2 * (p_s * q_s2 * N_s2 + p_w * q_w2 * N_w2 - c)) * dt
  #dE_test2 <- ((p_s2 * q_s2 * N_st2 + p_w2 * q_w2 * N_wt2) - c) * dt
  dC_s2 <- (q_s2 * N_s2 * E2) * dt
  dC_w2 <- (q_w2 * N_w2 * E2) * dt
  dcpue_s2 <- (C_s2 / E2) * dt
  dcpue_w2 <- (C_w2 / E2) * dt
  dPi_s2 <- (C_s2 * p_s - C_s2 * c) * dt
  dPi_w2 <- (C_w2 * p_w - C_w2 * c) * dt
  dPi2 <- (C_s2 * p_s + C_w2 * p_w - ((C_s2 + C_w2) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu2[i] <- N_w2 + dN_w2
  N_s_simu2[i] <- N_s2 + dN_s2
  #N_w_test_2[i] <- N_wt2 + dN_wt2
  #N_s_test_2[i] <- N_st2 + dN_st2
  E_simu2[i] <- E2 + dE2
  #E_test2[i] <- E_t2 + dE_test2
  C_s_simu2[i] <- C_s2 + dC_s2
  C_w_simu2[i] <- C_w2 + dC_w2
  cpue_s_simu2[i] <- cpue_s2 + dcpue_s2
  cpue_w_simu2[i] <- cpue_w2 + dcpue_w2
  Pi_sum_simu2[i] <- pi2 + dPi2
  Pi_s_simu2[i] <- pi_s2 + dPi_s2
  Pi_w_simu2[i] <- pi_w2 + dPi_w2  
  
  
}
```

```{r scenario 3 catchability ratio 2.5, echo = FALSE}
# set up the parameter space
q_s3 <- 0.9
q_w3 <- 0.36
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu3 <- NaN*tset; N_w_simu3[1] <- N_w

N_s_simu3 <- NaN*tset; N_s_simu3[1] <- N_s

#N_w_test_3 <- NaN*tset; N_w_test_3[1] <- N_w

#N_s_test_3 <- NaN*tset; N_s_test_3[1] <- N_s

E_simu3 <- NaN*tset; E_simu3[1] <- E

#E_test3 <- NaN*tset; E_test3[1] <- E

C_s_simu3 <- NaN*tset; C_s_simu3[1] <- 1

C_w_simu3 <- NaN*tset; C_w_simu3[1] <- 1

cpue_s_simu3 <- NaN*tset; cpue_s_simu3[1] <- 1

cpue_w_simu3 <- NaN*tset; cpue_w_simu3[1] <- 1

Pi_sum_simu3 <- NaN*tset; Pi_sum_simu3[1] <- 2

Pi_s_simu3 <- NaN*tset; Pi_s_simu3[1] <- 1

Pi_w_simu3 <- NaN*tset; Pi_w_simu3[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w3 <- N_w_simu3[i-1]
  N_s3 <- N_s_simu3[i-1]
  #N_wt3 <- N_w_test_3[i-1]
  #N_st3 <- N_s_test_3[i-1]
  E3 <- E_simu3[i-1]
  #E_t3 <- E_test3[i-1]
  C_s3 <- C_s_simu3[i-1]
  C_w3 <- C_w_simu3[i-1]
  cpue_s3 <- cpue_s_simu3[i-1]
  cpue_w3 <- cpue_w_simu3[i-1]
  pi3 <- Pi_sum_simu3[i-1]
  pi_s3 <- Pi_s_simu3[i-1]
  pi_w3 <- Pi_w_simu3[i-1]

  # Calculate change in variable size at each time step
  dN_s3 <- (N_s3 * (r_s * (1 - (N_s3/k_s)) - q_s3 * E3)) * dt
  dN_w3 <- (N_w3 * (r_w * (1 - (N_w3/k_w)) - q_w3 * E3)) * dt
  #dN_st3 <- (N_st3 * (r_s3 * (1 - (N_st3/k_s3)) - q_s3 * E_t3)) * dt
  #dN_wt3 <- (N_wt3 * (r_w3 * (1 - (N_wt3/k_w3)) - q_w3 * E_t3)) * dt
  dE3 <- (alpha * E3 * (p_s * q_s3 * N_s3 + p_w * q_w3 * N_w3 - c)) * dt
  #dE_test3 <- ((p_s3 * q_s3 * N_st3 + p_w3 * q_w3 * N_wt3) - c) * dt
  dC_s3 <- (q_s3 * N_s3 * E3) * dt
  dC_w3 <- (q_w3 * N_w3 * E3) * dt
  dcpue_s3 <- (C_s3 / E3) * dt
  dcpue_w3 <- (C_w3 / E3) * dt
  dPi_s3 <- (C_s3 * p_s - C_s3 * c) * dt
  dPi_w3 <- (C_w3 * p_w - C_w3 * c) * dt
  dPi3 <- (C_s3 * p_s + C_w3 * p_w - ((C_s3 + C_w3) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu3[i] <- N_w3 + dN_w3
  N_s_simu3[i] <- N_s3 + dN_s3
  #N_w_test_3[i] <- N_wt3 + dN_wt3
  #N_s_test_3[i] <- N_st3 + dN_st3
  E_simu3[i] <- E3 + dE3
  #E_test3[i] <- E_t3 + dE_test3
  C_s_simu3[i] <- C_s3 + dC_s3
  C_w_simu3[i] <- C_w3 + dC_w3
  cpue_s_simu3[i] <- cpue_s3 + dcpue_s3
  cpue_w_simu3[i] <- cpue_w3 + dcpue_w3
  Pi_sum_simu3[i] <- pi3 + dPi3
  Pi_s_simu3[i] <- pi_s3 + dPi_s3
  Pi_w_simu3[i] <- pi_w3 + dPi_w3  
  
  
}
```

```{r scenario 4 catchability ratio 1, echo = FALSE}
# set up the parameter space
q_s4 <- 0.5
q_w4 <- 0.5
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu4 <- NaN*tset; N_w_simu4[1] <- N_w

N_s_simu4 <- NaN*tset; N_s_simu4[1] <- N_s

#N_w_test_4 <- NaN*tset; N_w_test_4[1] <- N_w

#N_s_test_4 <- NaN*tset; N_s_test_4[1] <- N_s

E_simu4 <- NaN*tset; E_simu4[1] <- E

#E_test4 <- NaN*tset; E_test4[1] <- E

C_s_simu4 <- NaN*tset; C_s_simu4[1] <- 1

C_w_simu4 <- NaN*tset; C_w_simu4[1] <- 1

cpue_s_simu4 <- NaN*tset; cpue_s_simu4[1] <- 1

cpue_w_simu4 <- NaN*tset; cpue_w_simu4[1] <- 1

Pi_sum_simu4 <- NaN*tset; Pi_sum_simu4[1] <- 2

Pi_s_simu4 <- NaN*tset; Pi_s_simu4[1] <- 1

Pi_w_simu4 <- NaN*tset; Pi_w_simu4[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w4 <- N_w_simu4[i-1]
  N_s4 <- N_s_simu4[i-1]
  #N_wt4 <- N_w_test_4[i-1]
  #N_st4 <- N_s_test_4[i-1]
  E4 <- E_simu4[i-1]
  #E_t4 <- E_test4[i-1]
  C_s4 <- C_s_simu4[i-1]
  C_w4 <- C_w_simu4[i-1]
  cpue_s4 <- cpue_s_simu4[i-1]
  cpue_w4 <- cpue_w_simu4[i-1]
  pi4 <- Pi_sum_simu4[i-1]
  pi_s4 <- Pi_s_simu4[i-1]
  pi_w4 <- Pi_w_simu4[i-1]

  # Calculate change in variable size at each time step
  dN_s4 <- (N_s4 * (r_s * (1 - (N_s4/k_s)) - q_s4 * E4)) * dt
  dN_w4 <- (N_w4 * (r_w * (1 - (N_w4/k_w)) - q_w4 * E4)) * dt
  #dN_st4 <- (N_st4 * (r_s4 * (1 - (N_st4/k_s4)) - q_s4 * E_t4)) * dt
  #dN_wt4 <- (N_wt4 * (r_w4 * (1 - (N_wt4/k_w4)) - q_w4 * E_t4)) * dt
  dE4 <- (alpha * E4 * (p_s * q_s4 * N_s4 + p_w * q_w4 * N_w4 - c)) * dt
  #dE_test4 <- ((p_s4 * q_s4 * N_st4 + p_w4 * q_w4 * N_wt4) - c) * dt
  dC_s4 <- (q_s4 * N_s4 * E4) * dt
  dC_w4 <- (q_w4 * N_w4 * E4) * dt
  dcpue_s4 <- (C_s4 / E4) * dt
  dcpue_w4 <- (C_w4 / E4) * dt
  dPi_s4 <- (C_s4 * p_s - C_s4 * c) * dt
  dPi_w4 <- (C_w4 * p_w - C_w4 * c) * dt
  dPi4 <- (C_s4 * p_s + C_w4 * p_w - ((C_s4 + C_w4) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu4[i] <- N_w4 + dN_w4
  N_s_simu4[i] <- N_s4 + dN_s4
  #N_w_test_4[i] <- N_wt4 + dN_wt4
  #N_s_test_4[i] <- N_st4 + dN_st4
  E_simu4[i] <- E4 + dE4
  #E_test4[i] <- E_t4 + dE_test4
  C_s_simu4[i] <- C_s4 + dC_s4
  C_w_simu4[i] <- C_w4 + dC_w4
  cpue_s_simu4[i] <- cpue_s4 + dcpue_s4
  cpue_w_simu4[i] <- cpue_w4 + dcpue_w4
  Pi_sum_simu4[i] <- pi4 + dPi4
  Pi_s_simu4[i] <- pi_s4 + dPi_s4
  Pi_w_simu4[i] <- pi_w4 + dPi_w4  
  
  
}
```

```{r scenario 5 catchability ratio 0.75, echo = FALSE}
# set up the parameter space
q_s5 <- 0.9
q_w5 <- 0.9
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu5 <- NaN*tset; N_w_simu5[1] <- N_w

N_s_simu5 <- NaN*tset; N_s_simu5[1] <- N_s

#N_w_test_5 <- NaN*tset; N_w_test_5[1] <- N_w

#N_s_test_5 <- NaN*tset; N_s_test_5[1] <- N_s

E_simu5 <- NaN*tset; E_simu5[1] <- E

#E_test5 <- NaN*tset; E_test5[1] <- E

C_s_simu5 <- NaN*tset; C_s_simu5[1] <- 1

C_w_simu5 <- NaN*tset; C_w_simu5[1] <- 1

cpue_s_simu5 <- NaN*tset; cpue_s_simu5[1] <- 1

cpue_w_simu5 <- NaN*tset; cpue_w_simu5[1] <- 1

Pi_sum_simu5 <- NaN*tset; Pi_sum_simu5[1] <- 2

Pi_s_simu5 <- NaN*tset; Pi_s_simu5[1] <- 1

Pi_w_simu5 <- NaN*tset; Pi_w_simu5[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w5 <- N_w_simu5[i-1]
  N_s5 <- N_s_simu5[i-1]
  #N_wt5 <- N_w_test_5[i-1]
  #N_st5 <- N_s_test_5[i-1]
  E5 <- E_simu5[i-1]
  #E_t5 <- E_test5[i-1]
  C_s5 <- C_s_simu5[i-1]
  C_w5 <- C_w_simu5[i-1]
  cpue_s5 <- cpue_s_simu5[i-1]
  cpue_w5 <- cpue_w_simu5[i-1]
  pi5 <- Pi_sum_simu5[i-1]
  pi_s5 <- Pi_s_simu5[i-1]
  pi_w5 <- Pi_w_simu5[i-1]

  # Calculate change in variable size at each time step
  dN_s5 <- (N_s5 * (r_s * (1 - (N_s5/k_s)) - q_s5 * E5)) * dt
  dN_w5 <- (N_w5 * (r_w * (1 - (N_w5/k_w)) - q_w5 * E5)) * dt
  #dN_st5 <- (N_st5 * (r_s5 * (1 - (N_st5/k_s5)) - q_s5 * E_t5)) * dt
  #dN_wt5 <- (N_wt5 * (r_w5 * (1 - (N_wt5/k_w5)) - q_w5 * E_t5)) * dt
  dE5 <- (alpha * E5 * (p_s * q_s5 * N_s5 + p_w * q_w5 * N_w5 - c)) * dt
  #dE_test5 <- ((p_s5 * q_s5 * N_st5 + p_w5 * q_w5 * N_wt5) - c) * dt
  dC_s5 <- (q_s5 * N_s5 * E5) * dt
  dC_w5 <- (q_w5 * N_w5 * E5) * dt
  dcpue_s5 <- (C_s5 / E5) * dt
  dcpue_w5 <- (C_w5 / E5) * dt
  dPi_s5 <- (C_s5 * p_s - C_s5 * c) * dt
  dPi_w5 <- (C_w5 * p_w - C_w5 * c) * dt
  dPi5 <- (C_s5 * p_s + C_w5 * p_w - ((C_s5 + C_w5) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu5[i] <- N_w5 + dN_w5
  N_s_simu5[i] <- N_s5 + dN_s5
  #N_w_test_5[i] <- N_wt5 + dN_wt5
  #N_s_test_5[i] <- N_st5 + dN_st5
  E_simu5[i] <- E5 + dE5
  #E_test5[i] <- E_t5 + dE_test5
  C_s_simu5[i] <- C_s5 + dC_s5
  C_w_simu5[i] <- C_w5 + dC_w5
  cpue_s_simu5[i] <- cpue_s5 + dcpue_s5
  cpue_w_simu5[i] <- cpue_w5 + dcpue_w5
  Pi_sum_simu5[i] <- pi5 + dPi5
  Pi_s_simu5[i] <- pi_s5 + dPi_s5
  Pi_w_simu5[i] <- pi_w5 + dPi_w5  
  
  
}
```

```{r scenario 6 catchability ratio 0.5, echo = FALSE}
# set up the parameter space
q_s6 <- 0.45
q_w6 <- 0.9
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu6 <- NaN*tset; N_w_simu6[1] <- N_w

N_s_simu6 <- NaN*tset; N_s_simu6[1] <- N_s

#N_w_test_6 <- NaN*tset; N_w_test_6[1] <- N_w

#N_s_test_6 <- NaN*tset; N_s_test_6[1] <- N_s

E_simu6 <- NaN*tset; E_simu6[1] <- E

#E_test6 <- NaN*tset; E_test6[1] <- E

C_s_simu6 <- NaN*tset; C_s_simu6[1] <- 1

C_w_simu6 <- NaN*tset; C_w_simu6[1] <- 1

cpue_s_simu6 <- NaN*tset; cpue_s_simu6[1] <- 1

cpue_w_simu6 <- NaN*tset; cpue_w_simu6[1] <- 1

Pi_sum_simu6 <- NaN*tset; Pi_sum_simu6[1] <- 2

Pi_s_simu6 <- NaN*tset; Pi_s_simu6[1] <- 1

Pi_w_simu6 <- NaN*tset; Pi_w_simu6[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w6 <- N_w_simu6[i-1]
  N_s6 <- N_s_simu6[i-1]
  #N_wt6 <- N_w_test_6[i-1]
  #N_st6 <- N_s_test_6[i-1]
  E6 <- E_simu6[i-1]
  #E_t6 <- E_test6[i-1]
  C_s6 <- C_s_simu6[i-1]
  C_w6 <- C_w_simu6[i-1]
  cpue_s6 <- cpue_s_simu6[i-1]
  cpue_w6 <- cpue_w_simu6[i-1]
  pi6 <- Pi_sum_simu6[i-1]
  pi_s6 <- Pi_s_simu6[i-1]
  pi_w6 <- Pi_w_simu6[i-1]

  # Calculate change in variable size at each time step
  dN_s6 <- (N_s6 * (r_s * (1 - (N_s6/k_s)) - q_s6 * E6)) * dt
  dN_w6 <- (N_w6 * (r_w * (1 - (N_w6/k_w)) - q_w6 * E6)) * dt
  #dN_st6 <- (N_st6 * (r_s6 * (1 - (N_st6/k_s6)) - q_s6 * E_t6)) * dt
  #dN_wt6 <- (N_wt6 * (r_w6 * (1 - (N_wt6/k_w6)) - q_w6 * E_t6)) * dt
  dE6 <- (alpha * E6 * (p_s * q_s6 * N_s6 + p_w * q_w6 * N_w6 - c)) * dt
  #dE_test6 <- ((p_s6 * q_s6 * N_st6 + p_w6 * q_w6 * N_wt6) - c) * dt
  dC_s6 <- (q_s6 * N_s6 * E6) * dt
  dC_w6 <- (q_w6 * N_w6 * E6) * dt
  dcpue_s6 <- (C_s6 / E6) * dt
  dcpue_w6 <- (C_w6 / E6) * dt
  dPi_s6 <- (C_s6 * p_s - C_s6 * c) * dt
  dPi_w6 <- (C_w6 * p_w - C_w6 * c) * dt
  dPi6 <- (C_s6 * p_s + C_w6 * p_w - ((C_s6 + C_w6) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu6[i] <- N_w6 + dN_w6
  N_s_simu6[i] <- N_s6 + dN_s6
  #N_w_test_6[i] <- N_wt6 + dN_wt6
  #N_s_test_6[i] <- N_st6 + dN_st6
  E_simu6[i] <- E6 + dE6
  #E_test6[i] <- E_t6 + dE_test6
  C_s_simu6[i] <- C_s6 + dC_s6
  C_w_simu6[i] <- C_w6 + dC_w6
  cpue_s_simu6[i] <- cpue_s6 + dcpue_s6
  cpue_w_simu6[i] <- cpue_w6 + dcpue_w6
  Pi_sum_simu6[i] <- pi6 + dPi6
  Pi_s_simu6[i] <- pi_s6 + dPi_s6
  Pi_w_simu6[i] <- pi_w6 + dPi_w6  
  
  
}
```

```{r scenario 7 catchability ratio 0.25, echo = FALSE}
# set up the parameter space
q_s7 <- 0.225
q_w7 <- 0.9
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu7 <- NaN*tset; N_w_simu7[1] <- N_w

N_s_simu7 <- NaN*tset; N_s_simu7[1] <- N_s

#N_w_test_7 <- NaN*tset; N_w_test_7[1] <- N_w

#N_s_test_7 <- NaN*tset; N_s_test_7[1] <- N_s

E_simu7 <- NaN*tset; E_simu7[1] <- E

#E_test7 <- NaN*tset; E_test7[1] <- E

C_s_simu7 <- NaN*tset; C_s_simu7[1] <- 1

C_w_simu7 <- NaN*tset; C_w_simu7[1] <- 1

cpue_s_simu7 <- NaN*tset; cpue_s_simu7[1] <- 1

cpue_w_simu7 <- NaN*tset; cpue_w_simu7[1] <- 1

Pi_sum_simu7 <- NaN*tset; Pi_sum_simu7[1] <- 2

Pi_s_simu7 <- NaN*tset; Pi_s_simu7[1] <- 1

Pi_w_simu7 <- NaN*tset; Pi_w_simu7[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w7 <- N_w_simu7[i-1]
  N_s7 <- N_s_simu7[i-1]
  #N_wt7 <- N_w_test_7[i-1]
  #N_st7 <- N_s_test_7[i-1]
  E7 <- E_simu7[i-1]
  #E_t7 <- E_test7[i-1]
  C_s7 <- C_s_simu7[i-1]
  C_w7 <- C_w_simu7[i-1]
  cpue_s7 <- cpue_s_simu7[i-1]
  cpue_w7 <- cpue_w_simu7[i-1]
  pi7 <- Pi_sum_simu7[i-1]
  pi_s7 <- Pi_s_simu7[i-1]
  pi_w7 <- Pi_w_simu7[i-1]

  # Calculate change in variable size at each time step
  dN_s7 <- (N_s7 * (r_s * (1 - (N_s7/k_s)) - q_s7 * E7)) * dt
  dN_w7 <- (N_w7 * (r_w * (1 - (N_w7/k_w)) - q_w7 * E7)) * dt
  #dN_st7 <- (N_st7 * (r_s7 * (1 - (N_st7/k_s7)) - q_s7 * E_t7)) * dt
  #dN_wt7 <- (N_wt7 * (r_w7 * (1 - (N_wt7/k_w7)) - q_w7 * E_t7)) * dt
  dE7 <- (alpha * E7 * (p_s * q_s7 * N_s7 + p_w * q_w7 * N_w7 - c)) * dt
  #dE_test7 <- ((p_s7 * q_s7 * N_st7 + p_w7 * q_w7 * N_wt7) - c) * dt
  dC_s7 <- (q_s7 * N_s7 * E7) * dt
  dC_w7 <- (q_w7 * N_w7 * E7) * dt
  dcpue_s7 <- (C_s7 / E7) * dt
  dcpue_w7 <- (C_w7 / E7) * dt
  dPi_s7 <- (C_s7 * p_s - C_s7 * c) * dt
  dPi_w7 <- (C_w7 * p_w - C_w7 * c) * dt
  dPi7 <- (C_s7 * p_s + C_w7 * p_w - ((C_s7 + C_w7) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu7[i] <- N_w7 + dN_w7
  N_s_simu7[i] <- N_s7 + dN_s7
  #N_w_test_7[i] <- N_wt7 + dN_wt7
  #N_s_test_7[i] <- N_st7 + dN_st7
  E_simu7[i] <- E7 + dE7
  #E_test7[i] <- E_t7 + dE_test7
  C_s_simu7[i] <- C_s7 + dC_s7
  C_w_simu7[i] <- C_w7 + dC_w7
  cpue_s_simu7[i] <- cpue_s7 + dcpue_s7
  cpue_w_simu7[i] <- cpue_w7 + dcpue_w7
  Pi_sum_simu7[i] <- pi7 + dPi7
  Pi_s_simu7[i] <- pi_s7 + dPi_s7
  Pi_w_simu7[i] <- pi_w7 + dPi_w7  
  
  
}
```

```{r scenario 8 catchability ratio 0.1, echo = FALSE}
# set up the parameter space
q_s8 <- 0.09
q_w8 <- 0.9
```

```{r, echo = FALSE}
tset <- seq(from = 0, to = 500, length.out = 10000)

N_w_simu8 <- NaN*tset; N_w_simu8[1] <- N_w

N_s_simu8 <- NaN*tset; N_s_simu8[1] <- N_s

#N_w_test_8 <- NaN*tset; N_w_test_8[1] <- N_w

#N_s_test_8 <- NaN*tset; N_s_test_8[1] <- N_s

E_simu8 <- NaN*tset; E_simu8[1] <- E

#E_test8 <- NaN*tset; E_test8[1] <- E

C_s_simu8 <- NaN*tset; C_s_simu8[1] <- 1

C_w_simu8 <- NaN*tset; C_w_simu8[1] <- 1

cpue_s_simu8 <- NaN*tset; cpue_s_simu8[1] <- 1

cpue_w_simu8 <- NaN*tset; cpue_w_simu8[1] <- 1

Pi_sum_simu8 <- NaN*tset; Pi_sum_simu8[1] <- 2

Pi_s_simu8 <- NaN*tset; Pi_s_simu8[1] <- 1

Pi_w_simu8 <- NaN*tset; Pi_w_simu8[1] <- 1
```

```{r, echo = FALSE}
for(i in 2:length(tset)) {
  
  # change in time
  dt <- tset[i] - tset[i-1]
  
  # placeholder variables to plug into the equations
  N_w8 <- N_w_simu8[i-1]
  N_s8 <- N_s_simu8[i-1]
  #N_wt8 <- N_w_test_8[i-1]
  #N_st8 <- N_s_test_8[i-1]
  E8 <- E_simu8[i-1]
  #E_t8 <- E_test8[i-1]
  C_s8 <- C_s_simu8[i-1]
  C_w8 <- C_w_simu8[i-1]
  cpue_s8 <- cpue_s_simu8[i-1]
  cpue_w8 <- cpue_w_simu8[i-1]
  pi8 <- Pi_sum_simu8[i-1]
  pi_s8 <- Pi_s_simu8[i-1]
  pi_w8 <- Pi_w_simu8[i-1]

  # Calculate change in variable size at each time step
  dN_s8 <- (N_s8 * (r_s * (1 - (N_s8/k_s)) - q_s8 * E8)) * dt
  dN_w8 <- (N_w8 * (r_w * (1 - (N_w8/k_w)) - q_w8 * E8)) * dt
  #dN_st8 <- (N_st8 * (r_s8 * (1 - (N_st8/k_s8)) - q_s8 * E_t8)) * dt
  #dN_wt8 <- (N_wt8 * (r_w8 * (1 - (N_wt8/k_w8)) - q_w8 * E_t8)) * dt
  dE8 <- (alpha * E8 * (p_s * q_s8 * N_s8 + p_w * q_w8 * N_w8 - c)) * dt
  #dE_test8 <- ((p_s8 * q_s8 * N_st8 + p_w8 * q_w8 * N_wt8) - c) * dt
  dC_s8 <- (q_s8 * N_s8 * E8) * dt
  dC_w8 <- (q_w8 * N_w8 * E8) * dt
  dcpue_s8 <- (C_s8 / E8) * dt
  dcpue_w8 <- (C_w8 / E8) * dt
  dPi_s8 <- (C_s8 * p_s - C_s8 * c) * dt
  dPi_w8 <- (C_w8 * p_w - C_w8 * c) * dt
  dPi8 <- (C_s8 * p_s + C_w8 * p_w - ((C_s8 + C_w8) * c)) * dt
  
  # calculate total variable size and store in holding vectors
  
  N_w_simu8[i] <- N_w8 + dN_w8
  N_s_simu8[i] <- N_s8 + dN_s8
  #N_w_test_8[i] <- N_wt8 + dN_wt8
  #N_s_test_8[i] <- N_st8 + dN_st8
  E_simu8[i] <- E8 + dE8
  #E_test8[i] <- E_t8 + dE_test8
  C_s_simu8[i] <- C_s8 + dC_s8
  C_w_simu8[i] <- C_w8 + dC_w8
  cpue_s_simu8[i] <- cpue_s8 + dcpue_s8
  cpue_w_simu8[i] <- cpue_w8 + dcpue_w8
  Pi_sum_simu8[i] <- pi8 + dPi8
  Pi_s_simu8[i] <- pi_s8 + dPi_s8
  Pi_w_simu8[i] <- pi_w8 + dPi_w8  
  
  
}
```


```{r, echo = FALSE}
run_model <- function(r_s, k_s, q_s, p_s, r_w, k_w, q_w, p_w, c){
 
  # Derive effort
 E <- ((- c + k_s * p_s * q_s + k_w * p_w * q_w) * r_s * r_w)  /
   (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w) 
  
  # Derive weak stock biomass
 
  N_w <- (k_w * (c * q_w * r_s + k_s * p_s * q_s * (- q_w * r_s + q_s * r_w))) / 
    (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w)
  
 # Derive strong stock biomass
 
   N_s <- (k_s * (c * q_s * r_w + k_w * p_w * q_w * (q_w * r_s - q_s * r_w))) /
     (k_w * p_w * q_w^2 * r_s + k_s * p_s * q_s^2 * r_w)
  
  # Build output
  output <- data.frame(E = E, N_s = N_s, N_w = N_w)
 
  # Return
  return(output)
 
 
}

sc_q_1 <- run_model(q_s = 0.9, q_w = 0.09, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)
sc_q_2 <- run_model(q_s = 0.9, q_w = 0.18, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)
sc_q_3 <- run_model(q_s = 0.9, q_w = 0.36, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)
sc_q_4 <- run_model(q_s = 0.9, q_w = 0.9, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)
sc_q_5 <- run_model(q_s = 0.675, q_w = 0.9, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)
sc_q_6 <- run_model(q_s = 0.45, q_w = 0.9, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)
sc_q_7 <- run_model(q_s = 0.225, q_w = 0.9, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)
sc_q_8 <- run_model(q_s = 0.09, q_w = 0.9, k_s = 4, k_w = 2, r_s = 0.8, r_w = 0.45, p_s = 1, p_w = 1, c = 0.05)

sc_q_all <- bind_rows(sc_q_1, sc_q_2, sc_q_3, sc_q_4, sc_q_5, sc_q_6, sc_q_7, sc_q_8) %>% 
  rownames_to_column() %>% 
  rename(scenario = rowname) %>% 
  mutate(tset = 5) %>% 
  pivot_longer(cols = E:N_w,
               names_to = "variable",
               values_to = "value") %>% 
  mutate(q_ratio = case_when(
    scenario == "1" ~ "QR = 10",
    scenario == "2" ~ "QR = 5",
    scenario == "3" ~ "QR = 2.5",
    scenario == "4" ~ "QR = 1",
    scenario == "5" ~ "QR = 0.75",
    scenario == "6" ~ "QR = 0.5",
    scenario == "7" ~ "QR = 0.25",
    scenario == "8" ~ "QR = 0.1"
  )) %>% 
  pivot_wider(names_from = "variable",
              values_from = "value") %>% 
  mutate(b_values_s = N_s / k_s,
         b_values_w = N_w / k_w) %>% 
  pivot_longer(cols = N_s:N_w,
               names_to = "variable",
               values_to = "value") %>%
  pivot_longer(cols = b_values_s:b_values_w,
               names_to = "b_values",
               values_to = "b_v_k") %>% 
  pivot_longer(cols = E,
               names_to = "effort",
               values_to = "ef_value") %>% 
  mutate(variable = case_when(
    variable == "N_s" ~ "Ns*",
    variable == "N_w" ~ "Nw*"
  )) %>% 
  mutate(effort = case_when(
    effort == "E" ~ "E*"
  )) %>% 
  mutate(b_values = case_when(
    str_detect(b_values, "_w") ~ "Nw/Kw*",
    str_detect(b_values, "_s") ~ "Ns/Ks*"
  ))
```

```{r building df for the catchability parameter space, echo = FALSE}
eq_q_par <- data.frame(parameter = c("q_w", "q_s", "k_w", "k_s", "r_w", "r_s", "p_w", "p_s", "c"),
                     "QR_10" =  c(0.9, 0.09, 4, 2, 0.8, 0.45, 1, 1, 0.05),
                     "QR_5" =   c(0.9, 0.18, 4, 2, 0.8, 0.45, 1, 1, 0.05),
                     "QR_2.5" = c(0.9, 0.36, 4, 2, 0.8, 0.45, 1, 1, 0.05),
                     "QR_1" =   c(0.9, 0.9, 4, 2, 0.8, 0.45, 1, 1, 0.05),
                     "QR_0.75" =c(0.675, 0.9, 4, 2, 0.8, 0.45, 1, 1, 0.05),
                     "QR_0.5" = c(0.45, 0.9, 4, 2, 0.8, 0.45, 1, 1, 0.05),
                     "QR_0.25" =c(0.225, 0.9, 4, 2, 0.8, 0.45, 1, 1, 0.05),
                     "QR_0.1" = c(0.09, 0.9, 4, 2, 0.8, 0.45, 1, 1, 0.05))

eq_q_par %>% 
  gt() %>%
  tab_header(title = "Parameter space for equilibrium points") %>% 
  cols_align(align = "center")
  
```


```{r, echo = FALSE}
effort_df <- cbind(E_simu1, E_simu2, E_simu3, E_simu4, E_simu5, E_simu6, E_simu7, E_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("E_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8")
         )

# effort_test_df <- cbind(E_test1, E_test2, E_test3, E_test4, E_test5, E_test6, E_test7, E_test8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("E_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")
#     )

nw_df <- cbind(N_w_simu1, N_w_simu2, N_w_simu3, N_w_simu4, N_w_simu5, N_w_simu6, N_w_simu7,N_w_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("N_w_simu"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8")) %>% 
  mutate(b_v_k = value/k_w)


ns_df <- cbind(N_s_simu1, N_s_simu2, N_s_simu3, N_s_simu4, N_s_simu5, N_s_simu6, N_s_simu7, N_s_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("N_s_simu"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8")) %>% 
  mutate(b_v_k = value/k_s)

# ns_t_df <- cbind(N_s_test_1, N_s_test_2, N_s_test_3, N_s_test_4, N_s_test_5, N_s_test_6, N_s_test_7, N_s_test_8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("N_s_test_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")) %>% 
#   mutate(b_v_k = value/4)
# 
# nw_t_df <- cbind(N_w_test_1, N_w_test_2, N_w_test_3, N_w_test_4, N_w_test_5, N_w_test_6, N_w_test_7, N_w_test_8, tset) %>% 
#   as.data.frame() %>% 
#   pivot_longer(cols = starts_with("N_w_test_"),
#                names_to = "variable",
#                values_to = "value") %>% 
#   mutate(scenario_id = case_when(
#     str_detect(variable, "1") ~ "1",
#     str_detect(variable, "2") ~ "2",
#     str_detect(variable, "3") ~ "3",
#     str_detect(variable, "4") ~ "4",
#     str_detect(variable, "5") ~ "5",
#     str_detect(variable, "6") ~ "6",
#     str_detect(variable, "7") ~ "7",
#     str_detect(variable, "8") ~ "8")) %>% 
#   mutate(b_v_k = value/2)

catch_s_df <- cbind(C_s_simu1, C_s_simu2, C_s_simu3, C_s_simu4, C_s_simu5, C_s_simu6, C_s_simu7, C_s_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("C_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

catch_w_df <- cbind(C_w_simu1, C_w_simu2, C_w_simu3, C_w_simu4, C_w_simu5, C_w_simu6, C_w_simu7, C_w_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("C_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))


cpue_s_df <- cbind(cpue_s_simu1, cpue_s_simu2, cpue_s_simu3, cpue_s_simu4, cpue_s_simu5, cpue_s_simu6, cpue_s_simu7, cpue_s_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("cpue_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))


cpue_w_df <- cbind(cpue_w_simu1, cpue_w_simu2, cpue_w_simu3, cpue_w_simu4, cpue_w_simu5, cpue_w_simu6, cpue_w_simu7, cpue_w_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("cpue_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

profits_df <- cbind(Pi_sum_simu1, Pi_sum_simu2, Pi_sum_simu3, Pi_sum_simu4, Pi_sum_simu5, Pi_sum_simu6, Pi_sum_simu7, Pi_sum_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_sum"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

profits_s_df <- cbind(Pi_s_simu1, Pi_s_simu2, Pi_s_simu3, Pi_s_simu4, Pi_s_simu5, Pi_s_simu6, Pi_s_simu7, Pi_s_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_s_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

profits_w_df <- cbind(Pi_w_simu1, Pi_w_simu2, Pi_w_simu3, Pi_w_simu4, Pi_w_simu5, Pi_w_simu6, Pi_w_simu7, Pi_w_simu8, tset) %>% 
  as.data.frame() %>% 
  pivot_longer(cols = starts_with("Pi_w_"),
               names_to = "variable",
               values_to = "value") %>% 
  mutate(scenario_id = case_when(
    str_detect(variable, "1") ~ "1",
    str_detect(variable, "2") ~ "2",
    str_detect(variable, "3") ~ "3",
    str_detect(variable, "4") ~ "4",
    str_detect(variable, "5") ~ "5",
    str_detect(variable, "6") ~ "6",
    str_detect(variable, "7") ~ "7",
    str_detect(variable, "8") ~ "8"))

# Gathered the results from each model scenario run into a single df

var_full_q <- bind_rows(effort_df, nw_df, ns_df, catch_s_df, catch_w_df, cpue_s_df, cpue_w_df, profits_df, profits_w_df, profits_s_df)

# Tidy dataset for plotting

var_plot_q <- var_full_q %>%
  mutate(q_ratio = case_when(
    str_detect(scenario_id, "1") ~ "QR = 10",
    str_detect(scenario_id, "2") ~ "QR = 5",
    str_detect(scenario_id, "3") ~ "QR = 2.5",
    str_detect(scenario_id, "4") ~ "QR = 1",
    str_detect(scenario_id, "5") ~ "QR = 0.75",
    str_detect(scenario_id, "6") ~ "QR = 0.5",
    str_detect(scenario_id, "7") ~ "QR = 0.25",
    str_detect(scenario_id, "8") ~ "QR = 0.1"
  )) %>% 
  mutate(variable_clean = case_when(
    str_detect(variable, "N_w") ~ "Weak stock",
    str_detect(variable, "N_s") ~ "Strong stock",
    str_detect(variable, "E_simu") ~ "Effort simulation",
    str_detect(variable, "Pi_sum_") ~ "Profit sum",
    str_detect(variable, "Pi_s") ~ "Strong stock profits",
    str_detect(variable, "Pi_w") ~ "Weak stock profits",
    str_detect(variable, "cpue_w") ~ "Weak stock CPUE",
    str_detect(variable, "cpue_s") ~ "Strong stock CPUE",
    str_detect(variable, "C_w") ~ "Weak stock catch",
    str_detect(variable, "C_s") ~ "Strong stock catch"
  ))
```

```{r, echo = FALSE, fig.height=4, fig.width=8}
equal_scales_EWS_q <-
  var_plot_q %>% 
  filter(variable_clean %in% c("Effort simulation", "Weak stock", "Strong stock")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  geom_point(data = sc_q_all, 
             aes(x = tset, y = value, color = variable)) +
  geom_point(data = sc_q_all,
             aes(x = tset, y = ef_value, color = effort)) +
  facet_wrap(~ factor(q_ratio, 
                      levels = c("QR = 10",
                                 "QR = 5",
                                 "QR = 2.5",
                                 "QR = 1",
                                 "QR = 0.75",
                                 "QR = 0.5",
                                 "QR = 0.25",
                                 "QR = 0.1")),
             nrow = 1) +
  scale_color_manual(values = c("#1B9E77", "#1B9E77", "#D95F02", "#7570B3",  "#D95F02", "#7570B3")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "",
       y = "Nw, Ns, E",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

# equal_scales_EWS_test <-
#   var_plot %>% 
#   filter(variable_clean %in% c("Effort test", "Weak stock test", "Strong stock test")) %>% 
#   ggplot() +
#   geom_line(aes(x = tset/100, y = value, color = variable_clean),
#             size = .8,
#             alpha = .8,
#             show.legend = T) +
#   geom_point(data = sc_all, 
#              aes(x = tset, y = value, color = variable)) +
#   geom_point(data = sc_all, 
#              aes(x = tset, y = ef_value, color = effort)) +
#   facet_wrap(~ factor(price_ratio, 
#                       levels = c("PR = 10",
#                                  "PR = 5",
#                                  "PR = 2.5",
#                                  "PR = 1",
#                                  "PR = 0.75",
#                                  "PR = 0.5",
#                                  "PR = 0.25",
#                                  "PR = 0.1")),
#              nrow = 1) +
#   scale_color_manual(values = c("#1B9E77", "#1B9E77", "#D95F02", "#7570B3",  "#D95F02", "#7570B3")) +
# #  scale_y_continuous(breaks = seq(0, 50, 10)) +
#   labs(x = "",
#        y = "Nw, Ns, E",
#        color = "") +
#   theme_bw() +
#   theme(panel.grid.major.x = element_blank(),
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         strip.background = element_rect(fill = "transparent"),
#         strip.text = element_text(color = "black", size = 11),
#         axis.title.x = element_text(color = "black", size = 12),
#         axis.title.y = element_text(color = "black", size = 12, vjust = 2),
#         axis.text = element_text(color = "black", size = 10),
#         legend.position = "bottom")

dif_scales_q <-
  var_plot_q %>% 
  filter(variable_clean %in% c("Strong stock", "Weak stock")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = b_v_k, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = F) +
  geom_point(data = sc_q_all %>% filter(!variable == "E"), 
             aes(x = tset, y = b_v_k, color = b_values)) +
  facet_wrap(~ factor(q_ratio, 
                      levels = c("QR = 10",
                                 "QR = 5",
                                 "QR = 2.5",
                                 "QR = 1",
                                 "QR = 0.75",
                                 "QR = 0.5",
                                 "QR = 0.25",
                                 "QR = 0.1")),
             nrow = 1) +
  scale_color_manual(values = c("#D95F02", "#7570B3", "#D95F02", "#7570B3")) +
#  scale_x_continuous(breaks = seq(0, 500, 100)) +
  labs(x = "",
       y = "N/K (Nw, Ns)",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12, vjust = -2),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

equal_scales_CPE_q <-
  var_plot_q %>% 
  filter(variable_clean %in% c("Weak stock catch", "Strong stock catch", "Weak stock CPUE", "Strong stock CPUE")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  facet_wrap(~ factor(q_ratio, 
                      levels = c("QR = 10",
                                 "QR = 5",
                                 "QR = 2.5",
                                 "QR = 1",
                                 "QR = 0.75",
                                 "QR = 0.5",
                                 "QR = 0.25",
                                 "QR = 0.1")),
             nrow = 1) +
  scale_color_manual(values = c("#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "",
       y = "CPUE, Catch (S and W)",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")

equal_scales_pi_q <-
  var_plot_q %>% 
  filter(variable_clean %in% c("Profit sum", "Weak stock profits", "Strong stock profits")) %>% 
  ggplot() +
  geom_line(aes(x = tset/100, y = value, color = variable_clean),
            size = .8,
            alpha = .8,
            show.legend = T) +
  facet_wrap(~ factor(q_ratio, 
                      levels = c("QR = 10",
                                 "QR = 5",
                                 "QR = 2.5",
                                 "QR = 1",
                                 "QR = 0.75",
                                 "QR = 0.5",
                                 "QR = 0.25",
                                 "QR = 0.1")),
             nrow = 1) +
  scale_color_manual(values = c("#FF7F00", "#CAB2D6", "#6A3D9A")) +
#  scale_y_continuous(breaks = seq(0, 50, 10)) +
  labs(x = "Time (x100)",
       y = "Profits",
       color = "") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.background = element_rect(fill = "transparent"),
        strip.text = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 12),
        axis.title.y = element_text(color = "black", size = 12, vjust = 2),
        axis.text = element_text(color = "black", size = 10),
        legend.position = "bottom")
```

```{r, fig.height=15, fig.width=10, echo = FALSE}
equal_scales_EWS_q /
  dif_scales_q /
  equal_scales_CPE_q /
  equal_scales_pi_q +
  plot_annotation(tag_level = "A") 
```











